---
title: "k99_data_merging"
author: "Gavin Kelly"
date: "2025-06-06"
output: html_document
---

This is a data processing script for merging the k99 baseline, survey, and choicetask data.

I first merge the survey and choicetask data by subject and session. (line 41)

I then merge this with the baseline data by subject. (line 56)

Then i merge this with the ddm results by subject and session. (line 64)

I then save the csv. (line 72)

I also create an save a csv for data sharing, excluding identifiable variables (line 101).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("C:/Users/gavin/OneDrive - andrew.cmu.edu/Documents/RADLab")
```
  
  analysis vs synthetic data variables (vars have different names)
  
  Only in analysis:
    session
    specific event types and social contexts
    NA and PA state
    emotion change variables (predictive and retrospective)
    soft yday, today, intend, craving
    alc exp and mot overall
    date and time
    response, rt, rt_fast_prop
    day of week
    sex, student, education, employment, age
    baseline date and scale scores
    race gender sexuality nondectime

  Only in synthetic:
    none
    
  do we want weekend?
    

## Loading Data

```{r}
baseline_data_processed <- read.csv("baseline_data_processed.csv")
survey_data_processed <- read.csv("survey_data_processed.csv")
choicetask_data_processed <- read.csv("choicetask_data_processed.csv")
ddm_results_data <- read.csv("ddm_results.csv")
```

We can remove unnecessary columns from the ddm results data.

```{r}
ddm_results_data$negative_log_likelihood <- NULL
ddm_results_data$hit_boundary <- NULL
ddm_results_data$hit_boundary2 <- NULL
ddm_results_data$repr <- NULL
```

First we need to merge the survey and choice task data by "subject" and "session".

```{r}
survey_choicetask_merged_data <- left_join(survey_data_processed, choicetask_data_processed, by = c("subject", "session"))
```

```{r}
s_ct_ddm_merged_data <- left_join(survey_choicetask_merged_data, ddm_results_data, by = c("subject", "session"))
```

Now we can take this data frame and merge it with the baseline data by "subject".

```{r}
k99_merged_data <- left_join(s_ct_ddm_merged_data, baseline_data_processed, by = "subject")
```

Now we will edit the data file to make it appropriate for sharing, removing private info.

```{r}
k99_shared_data <- k99_merged_data[,!names(k99_merged_data) %in% c("alc_exp_none", "alc_mot_none", "race_hispanic_latino", "race_east_asian", "race_southeast_asian", "race_pacific_islander", "race_south_asian", "race_american_indian", "race_african_american", "race_african", "race_middle_eastern", "race_white", "race_other", "race_no_response", "gender_woman", "gender_man", "gender_trans_woman", "gender_trans_man", "gender_queer", "gender_agender", "gender_fluid",
"gender_intersex", "gender_non_binary","gender_other", "gender_no_response", "sexuality_lesbian", "sexuality_gay", "sexuality_bisexual", "sexuality_queer", "sexuality_two_spirit", "sexuality_straight", "sexuality_pansexual", "sexuality_asexual", "sexuality_no_response")]
```


```{r}
write.csv(k99_shared_data, "k99_shared_data.csv", row.names = F)
```







