---
title: "k99_drinks_project"
author: "Gavin Kelly"
date: "2025-07-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("C:/Users/gavin/OneDrive - andrew.cmu.edu/Documents/RADLab")
```

```{r}
library(dplyr)
library(lubridate)
library(tidyr)
library(psych)
library(ggplot2)
library(gghalves)
library(ggdist)
library(ggridges)
library(forcats)
library(reshape2)
library(cowplot)
library(ggpubr)
library(lme4)
library(sjstats)
library(gt)
library(webshot2)
```

## Loading Data

```{r}
# k99_shared_data <- read.csv("k99_shared_data.csv")
```

# Grouping Drinks


We can rename the alc images.

```{r}
# liquor, beer, seltzer, wine
k99_shared_data <- k99_shared_data %>%
  mutate(
    alc_image_name = case_when(
      alc_image == "alc01.jpg" ~ "Beer 2",
      alc_image == "alc02.jpg" ~ "Beer 1",
      alc_image == "alc03.jpg" ~ "Beer 3",
      alc_image == "alc04.jpg" ~ "Beer 4",
      alc_image == "alc05.jpg" ~ "Beer 6",
      alc_image == "alc06.jpg" ~ "Beer 5",
      alc_image == "alc07.jpg" ~ "IPA 1",
      alc_image == "alc08.jpg" ~ "IPA 2",
      alc_image == "alc09.jpg" ~ "Seltzer 3",
      alc_image == "alc10.jpg" ~ "Seltzer 4",
      alc_image == "alc11.jpg" ~ "Seltzer 1",
      alc_image == "alc12.jpg" ~ "Seltzer 2",
      alc_image == "alc13.jpg" ~ "White Wine 2",
      alc_image == "alc14.jpg" ~ "White Wine 1",
      alc_image == "alc15.jpg" ~ "Red Wine 1",
      alc_image == "alc16.jpg" ~ "Red Wine 2",
      alc_image == "alc17.jpg" ~ "Sparkling Wine",
      alc_image == "alc18.jpg" ~ "Vodka 1",
      alc_image == "alc19.jpg" ~ "Vodka 3",
      alc_image == "alc20.jpg" ~ "Vodka 2",
      alc_image == "alc21.jpg" ~ "Tequila 1",
      alc_image == "alc22.jpg" ~ "Tequila 3",
      alc_image == "alc23.jpg" ~ "Tequila 2",
      alc_image == "alc24.jpg" ~ "Gin 2",
      alc_image == "alc25.jpg" ~ "Gin 1",
      alc_image == "alc26.jpg" ~ "Bourbon",
      alc_image == "alc27.jpg" ~ "Whiskey 1",
      alc_image == "alc28.jpg" ~ "Whiskey 2",
      alc_image == "alc29.jpg" ~ "Rum 2",
      alc_image == "alc30.jpg" ~ "Rum 1"
    )
  )
```

And rename the soft drink images.

```{r}
#soda, diet soda, energy drink, juice, coffee
k99_shared_data <- k99_shared_data %>%
  mutate(
    soft_image_name = case_when(
      soft_image == "soft01.jpg" ~ "Soda 3", # "Coke"
      soft_image == "soft02.jpg" ~ "Diet Soda 2", # "Diet Coke"
      soft_image == "soft03.jpg" ~ "Diet Soda 1", # "Coke Zero"
      soft_image == "soft04.jpg" ~ "Soda 6", # "Pepsi"
      soft_image == "soft05.jpg" ~ "Diet Soda 4", # "Diet Pepsi"
      soft_image == "soft06.jpg" ~ "Diet Soda 5", # "Pepsi Zero"
      soft_image == "soft07.jpg" ~ "Soda 4", # "Dr Pepper"
      soft_image == "soft08.jpg" ~ "Diet Soda 3", # "Diet Dr Pepper"
      soft_image == "soft09.jpg" ~ "Soda 8", # "Sprite"
      soft_image == "soft10.jpg" ~ "Soda 1", # "7up"
      soft_image == "soft11.jpg" ~ "Soda 9", # "Sunkist"
      soft_image == "soft12.jpg" ~ "Soda 5", # "Mtn Dew"
      soft_image == "soft13.jpg" ~ "Soda 2", # "Canada Dry"
      soft_image == "soft14.jpg" ~ "Soda 7", # "Root Beer"
      soft_image == "soft15.jpg" ~ "Sweet Tea 1", # "Arizona (green)"
      soft_image == "soft16.jpg" ~ "Sweet Tea 2", # "Arizona (red)"
      soft_image == "soft17.jpg" ~ "Sweet Tea 3", # "Snapple"
      soft_image == "soft18.jpg" ~ "Sports Drink 1", # "Gatorade (orange)"
      soft_image == "soft19.jpg" ~ "Sports Drink 2", # "Gatorade (red)"
      soft_image == "soft20.jpg" ~ "Energy Drink 5", # "Monster"
      soft_image == "soft21.jpg" ~ "Energy Drink 3", # "Diet Monster"
      soft_image == "soft22.jpg" ~ "Energy Drink 6", # "Redbull"
      soft_image == "soft23.jpg" ~ "Energy Drink 4", # "Diet Redbull"
      soft_image == "soft24.jpg" ~ "Energy Drink 1", # "Celsius (lime)"
      soft_image == "soft25.jpg" ~ "Energy Drink 2", # "Celsius (orange)"
      soft_image == "soft26.jpg" ~ "Smoothie 2", # "Strawberry Smoothie"
      soft_image == "soft27.jpg" ~ "Smoothie 1", # "Mango Smoothie"
      soft_image == "soft28.jpg" ~ "Orange Juice", # "Orange Juice"
      soft_image == "soft29.jpg" ~ "Coffee 1", # "Coffee"
      soft_image == "soft30.jpg" ~ "Coffee 2" # "Frappuccino"
    )
  )
```

We can specify which type of alcoholic drink is presented for each choice.

```{r}
liquor_drinks <- c("Vodka 1", "Vodka 2", "Vodka 3", "Tequila 1", "Tequila 2", 
                   "Tequila 3", "Gin 1", "Gin 2", "Bourbon", "Whiskey 1",
                   "Whiskey 2", "Rum 1", "Rum 2")
beer_drinks <- c("Beer 1", "Beer 2", "Beer 3", "Beer 4", "Beer 5", "Beer 6",
                 "IPA 1", "IPA 2")
wine_drinks <- c("White Wine 1", "White Wine 2", "Red Wine 1", "Red Wine 2",
                 "Sparkling Wine")
seltzer_drinks <- c("Seltzer 1", "Seltzer 2", "Seltzer 3", "Seltzer 4")
k99_shared_data$alc_image_type = "none"
k99_shared_data <- k99_shared_data %>%
  mutate(
    alc_image_type = case_when(
      alc_image_name %in% liquor_drinks ~ "Liquor",
      alc_image_name %in% beer_drinks ~ "Beer",
      alc_image_name %in% wine_drinks ~ "Wine",
      alc_image_name %in% seltzer_drinks ~ "Seltzer"
    )
  )
```

We can specify which type of alcoholic drink is presented for each choice.

```{r}
sugary_drinks <- c("Soda 1", "Soda 2", "Soda 3", "Soda 4", "Soda 5", "Soda 6",
                 "Soda 7", "Soda 8", "Soda 9", "Sweet Tea 1", "Sweet Tea 2",
                 "Sweet Tea 3", "Sports Drink 1", "Sports Drink 2")
diet_soda_drinks <- c("Diet Soda 1", "Diet Soda 2", "Diet Soda 3", "Diet Soda 4", 
                      "Diet Soda 5")
energy_drinks <- c("Energy Drink 1", "Energy Drink 2", "Energy Drink 3", 
                   "Energy Drink 4", "Energy Drink 5", "Energy Drink 6")
juice_drinks <- c("Orange Juice", "Smoothie 1", "Smoothie 2")
coffee_drinks <- c("Coffee 1", "Coffee 2")
k99_shared_data$soft_image_type = "none"
k99_shared_data <- k99_shared_data %>%
  mutate(
    soft_image_type = case_when(
      soft_image_name %in% sugary_drinks ~ "Soda/Sugary Drink",
      soft_image_name %in% diet_soda_drinks ~ "Diet Soda",
      soft_image_name %in% energy_drinks ~ "Energy Drink",
      soft_image_name %in% juice_drinks ~ "Juice",
      soft_image_name %in% coffee_drinks ~ "Coffee"
    )
  )
```

# Descriptives for choices for alcohol and soft

We can look at the choices for alcohol and soft for each (type of) drink.

```{r}
# The SD is pretty high because there are some very low trial counts
k99_shared_data %>%
  ungroup() %>%
  group_by(alc_image_type, subject, session) %>%
  mutate(session_alc_response = sum(response == "alc", na.rm = T) / 
      (sum(response == "alc", na.rm = T) + sum(response == "soft", na.rm = T))) %>%
  group_by(alc_image_type, subject) %>%
  summarise(person_alc_response = sum(response == "alc", na.rm = T) / 
      (sum(response == "alc", na.rm = T) + sum(response == "soft", na.rm = T)),
      sd_session_responses = sd(session_alc_response, na.rm = T)) %>%
  group_by(alc_image_type) %>% #can also look by name
  summarise(overall_alc_responses = mean(person_alc_response, na.rm = T),
            sd_alc_responses = sd(person_alc_response, na.rm = T),
            avg_sd_within_person = mean(sd_session_responses, na.rm = T)) %>%
  arrange(overall_alc_responses)
```


```{r}
# The SD is pretty high because there are some very low trial counts
k99_shared_data %>%
  ungroup() %>%
  group_by(soft_image_type, subject, session) %>%
  mutate(session_soft_response = sum(response == "soft", na.rm = T) / 
      (sum(response == "alc", na.rm = T) + sum(response == "soft", na.rm = T))) %>%
  group_by(soft_image_type, subject) %>% #can also look by name
  mutate(person_soft_response = sum(response == "soft", na.rm = T) / 
      (sum(response == "alc", na.rm = T) + sum(response == "soft", na.rm = T)),
      sd_session_responses = sd(session_soft_response, na.rm = T)) %>%
  group_by(soft_image_type) %>%
  summarise(overall_soft_responses = mean(person_soft_response, na.rm = T),
      sd_overall_responses = sd(person_soft_response, na.rm = T),
      avg_sd_within_person = mean(sd_session_responses, na.rm = T)) %>%
  arrange(overall_soft_responses)
#show example for different types of people, one plot for each person
#could plot from day to day, time series plot
#one is consistent, another all over, another always below 50
```

# prop choices for each drink type by value function

```{r}
k99_shared_data %>% 
  group_by(alc_image_type) %>%
  summarise(prop_choices = sum(response == "alc", na.rm = T)/sum(!is.na(response)))
```
```{r}
#check when val fn == 0
k99_shared_data %>% 
  filter(value_function == 0) %>% group_by(alc_image_type) %>%
  summarise(prop_choices = sum(response == "alc", na.rm = T)/sum(!is.na(response)))
```
```{r}
k99_shared_data %>% 
  group_by(soft_image_type) %>%
  summarise(prop_choices = sum(response == "soft", na.rm = T)/sum(!is.na(response)))
```
```{r}
#check when val fn == 0
k99_shared_data %>% 
  filter(value_function == 0) %>% group_by(soft_image_type) %>%
  summarise(prop_choices = sum(response == "soft", na.rm = T)/sum(!is.na(response)))
```
# time lag drinking behavior

```{r}
#check when val fn == 0
k99_shared_data %>% 
  filter(value_function == 0) %>% group_by(alc_image_type) %>%
  summarise(prop_choices = sum(response == "alc", na.rm = T)/sum(!is.na(response)))
```

```{r}
# first we need to create a new df
ema_lead_grid <- expand.grid(
  subject = 1:250,
  day_number = 1:14
)
#add day num to merged with days since baseline
k99_lead_data <- k99_shared_data %>%
  filter(!is.na(response)) %>%
  group_by(subject, session) %>%
  mutate(prop_soda_responses = sum(response == "soft" & soft_image_type == "Soda/Sugary Drink") /
           sum(soft_image_type == "Soda/Sugary Drink"),
         prop_diet_soda_responses = sum(response == "soft" & soft_image_type == "Diet Soda") /
           sum(soft_image_type == "Diet Soda"),
         prop_juice_responses = sum(response == "soft" & soft_image_type == "Juice") /
           sum(soft_image_type == "Juice"),
         prop_energy_responses = sum(response == "soft" & soft_image_type == "Energy Drink") /
           sum(soft_image_type == "Energy Drink"),
         prop_coffee_responses = sum(response == "soft" & soft_image_type == "Coffee") /
           sum(soft_image_type == "Coffee"),
         
         prop_beer_responses = sum(response == "alc" & alc_image_type == "Beer") /
           sum(alc_image_type == "Beer"),
         prop_liquor_responses = sum(response == "alc" & alc_image_type == "Liquor") /
           sum(alc_image_type == "Liquor"),
         prop_seltzer_responses = sum(response == "alc" & alc_image_type == "Seltzer") /
           sum(alc_image_type == "Seltzer"),
         prop_wine_responses = sum(response == "alc" & alc_image_type == "Wine") /
           sum(alc_image_type == "Wine"),
         
         prop_preference_reversals = (sum(response == "alc" & value_function < 0, na.rm = T) + 
                                      sum(response == "soft" & value_function > 0, na.rm = T))/
                                      sum(!is.na(response))) %>%
  group_by(subject) %>%
  mutate(date = as.Date(date, format = "%Y-%m-%d"),
         baseline_date = as.Date(end_date_string, format = "%m/%d/%Y"),
         day_number = as.numeric(difftime(date, baseline_date, units = "days")),
         hour = hour(hms(time))) %>%
  mutate(
    day_number = ifelse(day_number >= 1 & day_number <= 14, day_number, NA)
  )
```

```{r}
k99_lead_data <- k99_lead_data[c("subject", "session", "day_number", "alc_yday",
                                 "alc_intend", "prop_alc_responses", 
                     "prop_soda_responses", "prop_diet_soda_responses",
                     "prop_juice_responses", "prop_energy_responses",
                     "prop_coffee_responses", "prop_beer_responses",
                     "prop_liquor_responses", "prop_seltzer_responses",
                     "prop_wine_responses", "time_of_day",
                     "audit_score", "age", "day_of_week",
                     "thirst_state", "hunger_state", "tired_state",
                     "bored_state", "alc_craving", "soft_craving",
                     "social_context_overall", "location", "alc_cue",
                     "responsibility", "hour", "prop_preference_reversals")]

ema_lead <- ema_lead_grid %>%
  left_join(k99_lead_data, by = c("subject", "day_number"))

ema_lead <- ema_lead %>%
  group_by(subject, session, day_number) %>%
  slice(1) %>%
  ungroup() %>%
  arrange(subject, day_number) %>%
  ungroup()
```

```{r}
#for some reason when they are all NA, min returns Inf, so i have to fix that
ema_lead <- ema_lead %>%
  group_by(subject, day_number) %>%
  mutate(alc_yday = min(alc_yday, na.rm = T)) %>%
  mutate(alc_yday = case_when(
    alc_yday == "Inf" ~ NA,
    TRUE ~ alc_yday
  ))
```

```{r}
alc_yday_shifted <- ema_lead %>%
  group_by(subject, day_number) %>%
  summarise(alc_yday_day = first(alc_yday), .groups = "drop") %>%
  arrange(subject, day_number) %>%
  group_by(subject) %>%
  mutate(alc_consumed_today = lead(alc_yday_day))  # shift back one day

# Join this shifted value back to the original session-level data
ema_lead <- ema_lead %>%
  left_join(alc_yday_shifted %>% select(subject, day_number, alc_consumed_today),
            by = c("subject", "day_number"))
```

# Descriptives for drinking behavior

```{r}
ema_lead %>% ungroup() %>% summarise(prop = sum(alc_consumed_today > 0, na.rm = T) / sum(!is.na(alc_consumed_today))) # prop study days drinking
ema_lead %>% ungroup() %>% filter(alc_consumed_today > 0) %>%
  summarise(avg_num_drinks = mean(alc_consumed_today, na.rm = T)) # avg num drinks
```


```{r}
cor(ema_lead$alc_intend, ema_lead$prop_alc_responses, use = "complete.obs")
cor(ema_lead$alc_consumed_today, ema_lead$prop_alc_responses, use = "complete.obs")
```

```{r}
# look at difference in correlations between afternoon and evening
ema_lead %>%
  filter(!is.na(time_of_day)) %>%
  group_by(time_of_day) %>%
  summarise(
    cor_consumed_prop = cor(alc_consumed_today, prop_alc_responses, use = "complete.obs"),
    cor_intend_prop = cor(alc_intend, prop_alc_responses, use = "complete.obs")
  )
```

```{r}
cor_df <- ema_lead %>%
  group_by(subject) %>%
  mutate(
    mean_prop_alc_responses = mean(prop_alc_responses, na.rm = T),
    mean_alc_intend = mean(alc_intend, na.rm = T), 
    mean_alc_consumed = mean(alc_consumed_today, na.rm = T)
  ) %>%
  slice(1)
```

```{r}
cor_df <- cor_df[c("mean_prop_alc_responses", "mean_alc_intend", "mean_alc_consumed",
                   "audit_score", "age")]
cor_matrix <- cor_df %>%
  cor(use = "pairwise.complete.obs") %>% 
  round(., 2)
cor_matrix
```

```{r}
cor_df2 <- ema_lead[c("prop_alc_responses", "alc_intend", "alc_consumed_today",
                      "alc_craving", "thirst_state", "tired_state",
                   "hunger_state", "bored_state")]
cor_matrix2 <- cor_df2 %>%
  cor(use = "pairwise.complete.obs") %>% 
  round(., 2)
cor_matrix2
```

```{r}
cor_df3 <- ema_lead %>%
  group_by(subject) %>%
  mutate(
    mean_prop_soda_responses = mean(prop_soda_responses, na.rm = T),
    mean_prop_diet_soda_responses = mean(prop_diet_soda_responses, na.rm = T),
    mean_prop_juice_responses = mean(prop_juice_responses, na.rm = T),
    mean_prop_energy_responses = mean(prop_energy_responses, na.rm = T),
    mean_prop_coffee_responses = mean(prop_coffee_responses, na.rm = T),
    
    mean_prop_beer_responses = mean(prop_beer_responses, na.rm = T),
    mean_prop_liquor_responses = mean(prop_liquor_responses, na.rm = T),
    mean_prop_seltzer_responses = mean(prop_seltzer_responses, na.rm = T),
    mean_prop_wine_responses = mean(prop_wine_responses, na.rm = T),
    
    mean_alc_intend = mean(alc_intend, na.rm = T), 
    mean_alc_consumed = mean(alc_consumed_today, na.rm = T)
  ) %>%
  slice(1)
```

```{r}
cor_df3 <- cor_df3[c("mean_prop_soda_responses", "mean_prop_diet_soda_responses",
                     "mean_prop_juice_responses", "mean_prop_energy_responses",
                     "mean_prop_coffee_responses", "mean_prop_beer_responses",
                     "mean_prop_liquor_responses", "mean_prop_seltzer_responses",
                     "mean_prop_wine_responses", "mean_alc_intend", "mean_alc_consumed",
                   "audit_score", "age")]
cor_matrix3 <- cor_df3 %>%
  cor(use = "pairwise.complete.obs") %>% 
  round(., 2)
cor_matrix3
```

```{r}
cor_df4 <- ema_lead[c("prop_soda_responses", "prop_diet_soda_responses",
                     "prop_juice_responses", "prop_energy_responses",
                     "prop_coffee_responses", "prop_beer_responses",
                     "prop_liquor_responses", "prop_seltzer_responses",
                     "prop_wine_responses", "alc_intend",
                     "alc_consumed_today", "alc_craving", "soft_craving",
                     "thirst_state")]
cor_matrix4 <- cor_df4 %>%
  cor(use = "pairwise.complete.obs") %>% 
  round(., 2)
cor_matrix4
```

# prop choices by drink pairings

```{r}
#calculate the study wide prop choices for drink type pairings.
pairs_dat <- k99_shared_data %>%
  group_by(alc_image_type, soft_image_type) %>%
  mutate(prop_alc_choices = sum(response == "alc", na.rm = T) / sum(!is.na(response))) %>%
  slice(1)
```

# plot choice pairings of drink types

```{r}
ggplot(pairs_dat, aes(x = soft_image_type, y = prop_alc_choices, fill = alc_image_type, 
        color = alc_image_type, group = alc_image_type)) +
  stat_summary(aes(group = alc_image_type), fun = mean, geom = "point", size = 6) +
  stat_summary(aes(group = alc_image_type), fun = mean, geom = "line", size = 3) +
  scale_color_manual(values = alc_colors) +
  labs(x = "Drink Type", y = "Proportion of Choices", title = "") +
  theme_cowplot() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
```


# plot number of observations by value function

```{r}
#descriptive for num obs, avg rating difference
k99_shared_data %>% group_by(alc_image_type) %>% 
  summarise(n = sum(!is.na(response)), avg_rating_dif = mean(value_function, na.rm = T))
```

```{r}
alc_colors <- c("Beer" = "#003049", "Wine" = "#f77f00", "Seltzer" = "#fcbf49", "Liquor" = "#d62828")

prop_obs_dat <- k99_shared_data %>%
  ungroup() %>%
  group_by(alc_image_type) %>%
  mutate(total_n = sum(!is.na(response))) %>%
  ungroup() %>%
  group_by(alc_image_type, value_function) %>%
  mutate(prop_obs_val = sum(!is.na(response))/total_n) %>%
  slice(1)

prop_obs_dat$alc_image_type <- factor(prop_obs_dat$alc_image_type, 
                                   levels = c("Liquor", "Beer", "Wine", "Seltzer"))

prop_obs_plot <- ggplot(prop_obs_dat, aes(x = value_function, y = prop_obs_val, 
                   color = alc_image_type, group = alc_image_type)) +
    geom_point(size = 7) +
    geom_line(size = 3) +
    theme_cowplot() +
    scale_fill_manual(values = alc_colors) +
    scale_color_manual(values = alc_colors) +
    theme(
      axis.text.x = element_text(size = 16),
      axis.title.x = element_text(size = 18),
      axis.ticks.x = element_blank(),
      axis.text.y = element_text(size = 14),
      axis.title.y = element_text(size = 18)
    ) +
    scale_x_continuous(breaks = seq(-3, 3, by = 1))+ 
  labs(  title = "", x = "Value Function", y = "Proportion of Observations",
  color = "Drink Type")
prop_obs_plot
```

```{r}
# ggsave("prop_obs_plot.jpeg", prop_obs_plot, device = "jpeg", width = 7, height = 5, dpi = 300)
```

# avg increase in choices by value fn

```{r}
k99_shared_data %>%
  group_by(alc_image_type, value_function) %>%
  summarise(choices = sum(response == "alc", na.rm = T)/
                  sum(!is.na(response))) %>%
  group_by(alc_image_type) %>%
  summarise(avg_increase = (max(choices) - min(choices)) / 6)
```


# create table for choices for drinks by value function

```{r}
k99_long_data <- k99_shared_data %>%
  group_by(value_function, alc_image_type) %>%
  mutate(avg_responses = sum(response == "alc", na.rm = T)/
                              sum(!is.na(response))) %>%
  slice(1) %>%
  select(avg_responses, alc_image_type, value_function)
k99_long_data$alc_image_type <- factor(k99_long_data$alc_image_type,
  levels = c("Liquor", "Wine", "Beer", "Seltzer"))
k99_long_data <- rename(k99_long_data, "Drink Type" = alc_image_type)
k99_long_data <- rename(k99_long_data, "Rating Difference" = value_function)
```

```{r}
# Using the same my_dataframe
drink_val_tab <- xtabs(avg_responses ~ `Drink Type` + `Rating Difference`, data = k99_long_data)
drink_val_tab_df <- as.data.frame.matrix(drink_val_tab)
drink_val_tab_df <- tibble::rownames_to_column(drink_val_tab_df, var = "Drink Type")
```

```{r}
final_drink_val_tab <- drink_val_tab_df %>%
  gt() %>%
  tab_header(title = "Average Responses by Drink Type and Rating Difference") %>%
  fmt_number(columns = everything(), decimals = 2) %>%
  tab_options(table.font.size = 14)
```

```{r}
gtsave(final_drink_val_tab, "drink_val_table.png", zoom = 2)
```


```{r}
k99_long_soft_data <- k99_shared_data %>%
  group_by(value_function, soft_image_type) %>%
  mutate(avg_responses = sum(response == "soft", na.rm = T)/
                              sum(!is.na(response))) %>%
  slice(1) %>%
  select(avg_responses, soft_image_type, value_function)

k99_long_soft_data$soft_image_type <- factor(k99_long_soft_data$soft_image_type,
  levels = c("Coffee", "Energy Drink", "Juice", "Diet Soda", "Soda/Sugary Drink"))

k99_long_soft_data <- rename(k99_long_soft_data, "Drink Type" = soft_image_type)
k99_long_soft_data <- rename(k99_long_soft_data, "Rating Difference" = value_function)
```

# function for plotting prop choices by value function

```{r}
plot_drink_values <- function(data, colors){
  ggplot(data, aes(x = `Rating Difference`, y = avg_responses, 
                   color = `Drink Type`, group = `Drink Type`)) +
    geom_line(size = 2.5) +
    geom_point(size = 5) +
    theme_cowplot() +
    scale_fill_manual(values = colors) +
    scale_color_manual(values = colors) +
    theme(
      axis.text.x = element_text(size = 16),
      axis.title.x = element_text(size = 18),
      axis.ticks.x = element_blank(),
      axis.text.y = element_text(size = 14),
      axis.title.y = element_text(size = 18)
    ) +
    scale_x_continuous(breaks = seq(-3, 3, by = 1)) +
    ylim(0, 1)
}
```

# plot prop choices by value function


```{r}
alc_drinks_value_plot <- plot_drink_values(
  data = k99_long_data,
  colors = alc_colors
) + labs(
  title = "",
  x = "Value Function",
  y = "Choices for Alcohol (%)",
  color = "Drink Type"
)

alc_drinks_value_plot
```





```{r}
soft_colors <- c("Soda/Sugary Drink" = "#2364aa", "Diet Soda" = "#3da5d9", "Coffee" = "#b298dc",
                 "Energy Drink" = "#662e9b", "Juice" = "#8f2d56")
soft_drinks_value_plot <- plot_drink_values(
  data = k99_long_soft_data,
  colors = soft_colors
) + labs(
  title = "",
  x = "Value Function",
  y = "Choices for Soft Drinks (%)",
  color = "Drink Type"
)

soft_drinks_value_plot
```

```{r}
drinks_value_plot <- ggpubr::ggarrange(
  alc_drinks_value_plot, soft_drinks_value_plot,
  ncol = 2,
  nrow = 1,
  widths = c(2.62, 3),
  labels = c("A", "B"),
  font.label = list(size = 18, face = "bold"), # Optional formatting
  label.x = 0,
  label.y = 1
)
ggsave("drinks_value_plot.jpeg", drinks_value_plot, device = "jpeg", width = 12, height = 4, dpi = 300)
```



# calculate ICC

```{r}
model_icc <- function(dat, formula){
  lmer(formula, data = dat) }
performance::icc(model_icc(ema_lead, prop_alc_responses ~ 1 + (1|subject)))
performance::icc(model_icc(ema_lead, prop_liquor_responses ~ 1 + (1|subject)))
performance::icc(model_icc(ema_lead, prop_wine_responses ~ 1 + (1|subject)))
performance::icc(model_icc(ema_lead, prop_beer_responses ~ 1 + (1|subject)))
performance::icc(model_icc(ema_lead, prop_seltzer_responses ~ 1 + (1|subject)))
```

# calculate overall SD and for drink types

```{r}
ema_lead %>%
  group_by(subject) %>%
  summarise(sd_choices = sd(prop_alc_responses, na.rm = T)) %>%
  ungroup() %>%
  summarise(avg_sd = mean(sd_choices, na.rm = T),
            min_sd = min(sd_choices, na.rm = T),
            max_sd = max(sd_choices, na.rm = T),
            sd_sd = sd(sd_choices, na.rm = T))
```

```{r}
ema_long %>%
  group_by(subject, drink_type) %>%
  summarise(sd_choices = sd(prop_drink_type_responses, na.rm = T)) %>%
  group_by(drink_type) %>%
  summarise(avg_sd = mean(sd_choices, na.rm = T),
            min_sd = min(sd_choices, na.rm = T),
            max_sd = max(sd_choices, na.rm = T),
            sd_sd = sd(sd_choices, na.rm = T))
```

# Day Number Within Person Variability Plot

```{r}
clr = "#5c677d"
day_num_plot <- ggplot(ema_lead, aes(x = day_number, y = prop_alc_responses, 
                                    fill = clr, color = clr)) +
  geom_point(size = 2, alpha = 0.1, width = .35, height = .25) +
  geom_line(aes(group = subject), alpha = 0.1) +
  stat_summary( fun = mean, geom = "point", size = 6, color = "black") +
  stat_summary( fun = mean, geom = "line", size = 3, color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5, color = "black") +
  # geom_point(aes(x = day_number, y = prop_alc_responses), size = 7, color = "#001233") +
  # geom_line(aes(x = day_number, y = prop_alc_responses), size = 3, color = "#001233") +
  theme_cowplot() +
  scale_fill_manual(values = clr) +
  scale_color_manual(values = clr) +
    theme(
      legend.position = "none",
      axis.text.x = element_text(size = 16),
      axis.title.x = element_text(size = 18),
      axis.ticks.x = element_blank(),
      axis.text.y = element_text(size = 14),
      axis.title.y = element_text(size = 18)
    ) +
  scale_x_continuous(breaks = seq(1, 14, by = 1)) +
  scale_y_continuous(breaks = seq(0, 1, by = .25)) +
  coord_cartesian(xlim = c(1, 14), ylim = c(0, 1)) +
  labs(title = "", x = "Day Number", y = "Choices for Alcohol (%)")
day_num_plot
```

# Preference Reversal Plot

```{r}
clr = "#5c677d"
pref_rev_plot <- ggplot(ema_lead, aes(x = day_number, y = prop_preference_reversals, 
                                    fill = clr, color = clr)) +
  geom_point(size = 2, alpha = 0.1, width = .35, height = .25) +
  geom_line(aes(group = subject), alpha = 0.1) +
  stat_summary( fun = mean, geom = "point", size = 6, color = "black") +
  stat_summary( fun = mean, geom = "line", size = 3, color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5, color = "black") +
  # geom_point(aes(x = day_number, y = prop_alc_responses), size = 7, color = "#001233") +
  # geom_line(aes(x = day_number, y = prop_alc_responses), size = 3, color = "#001233") +
  theme_cowplot() +
  scale_fill_manual(values = clr) +
  scale_color_manual(values = clr) +
    theme(
      legend.position = "none",
      axis.text.x = element_text(size = 16),
      axis.title.x = element_text(size = 18),
      axis.ticks.x = element_blank(),
      axis.text.y = element_text(size = 14),
      axis.title.y = element_text(size = 18)
    ) +
  scale_x_continuous(breaks = seq(1, 14, by = 1)) +
  scale_y_continuous(breaks = seq(0, 1, by = .25)) +
  coord_cartesian(xlim = c(1, 14), ylim = c(0, 1)) +
  labs(title = "", x = "Day Number", y = "Preference Reversals (%)")
pref_rev_plot
```

```{r}
ggsave("pref_rev_plot.jpeg", pref_rev_plot, device = "jpeg", width = 9,
       height = 5, dpi = 300)
```

# Day of Week Choices for Alcohol Plot

```{r}
highlight_subjects <- c(50, 14, 10, 202)  # replace with actual IDs

# Add a new column to mark which subject to highlight
ema_lead$highlight <- ifelse(ema_lead$subject %in% highlight_subjects, 
                              as.character(ema_lead$subject), "Other")

# Convert highlight to a factor so colors are consistent
ema_lead$highlight <- factor(ema_lead$highlight, levels = c("Other", highlight_subjects))

# Define colors for each
highlight_colors <- c("Other" = "#a67ba0", 
                      "50" = "orange", 
                      "14" = "#0072B2", 
                      "10" = "#009E73",
                      "202" = "red")
ema_days <- ema_lead
ema_days$subject <- as.factor(ema_days$subject)
```


```{r}
day_of_week_plot <- ggplot(subset(ema_lead, !is.na(day_of_week)), 
       aes(x = day_of_week, y = prop_alc_responses, group = subject)) +
 geom_line(color = "#a67ba0", alpha = 0.1) +
  geom_point(color = "#a67ba0", size = 1.5, alpha = 0.3) +
  
  # Mean line across all subjects
  stat_summary(aes(group = 1), fun = mean, geom = "point", size = 6, color = "#800870") +
  stat_summary(aes(group = 1), fun = mean, geom = "line", size = 3, color = "#800870") +

  scale_color_manual(values = highlight_colors) +
  theme_cowplot() +
  theme(
    legend.title = element_blank(),
    legend.position = "right",
    axis.text.x = element_text(size = 16),
    axis.title.x = element_text(size = 18),
    axis.ticks.x = element_blank(),
    axis.text.y = element_text(size = 14),
    axis.title.y = element_text(size = 18)
  ) +
  scale_y_continuous(breaks = seq(0, 1, by = .25)) +
  labs(x = "Day of Week", y = "Choices for Alcohol (%)")

day_of_week_plot
```

```{r}
ggsave("day_of_week_plot.jpeg", day_of_week_plot, device = "jpeg", width = 7,
       height = 4, dpi = 300)
```

# drinking behavior weekly statistics

```{r}
ema_week <- ema_lead %>%
  mutate(weekend = case_when(
    day_of_week %in% c("Fri", "Sat") ~ "Weekend",
    !is.na(day_of_week) ~ "Weekday"
  ))
ema_week %>%
  filter(!is.na(alc_consumed_today) & !is.na(prop_alc_responses)) %>%
  group_by(weekend) %>%
  summarise(consumed_mean = mean(alc_consumed_today, na.rm = T),
            consumed_sd = sd(alc_consumed_today, na.rm = T),
            consumed_min = min(alc_consumed_today, na.rm = T),
            consumed_max = max(alc_consumed_today, na.rm = T),
            corsd = cor(alc_consumed_today, prop_alc_responses),
            mean_choices = mean(prop_alc_responses, na.rm = T),
            sd_choices = sd(prop_alc_responses, na.rm = T),
            min_choices = min(prop_alc_responses, na.rm = T),
            max_choices = max(prop_alc_responses, na.rm = T))
```


# Hourly Choices for Alcohol Plot

```{r}
clr = "#a67ba0"
hours_plot <- ggplot(subset(ema_lead, hour >= 15 & hour < 23), aes(x = hour, y = prop_alc_responses, 
                                    fill = clr, color = clr)) +
  geom_point(size = 2, alpha = 0.1, width = .35, height = .25) +
  geom_line(aes(group = subject), alpha = 0.1) +
  stat_summary(aes(group = 1), fun = mean, geom = "point", size = 6, color = "#800870") +
  stat_summary(aes(group = 1), fun = mean, geom = "line", size = 3, color = "#800870") +
  theme_cowplot() +
  scale_fill_manual(values = clr) +
  scale_color_manual(values = clr) +
  # facet_wrap(~ day_of_week, ncol = 1) +
    theme(
      legend.position = "none",
      axis.text.x = element_text(size = 16),
      axis.title.x = element_text(size = 18),
      axis.ticks.x = element_blank(),
      axis.text.y = element_text(size = 14),
      axis.title.y = element_text(size = 18)
    ) +
  scale_y_continuous(breaks = seq(0, 1, by = .25)) +
  labs(title = "", x = "Hour", y = "Choices for Alcohol (%)")
hours_plot
```

```{r}
# ggsave("hours_plot.jpeg", hours_plot, device = "jpeg", width = 7,
#        height = 4, dpi = 300)
```


# Day of Week Choices for Alcohol type Plot


```{r}
ema_long$day_of_week <- factor(ema_long$day_of_week,
  levels = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"))
day_of_week_type_plot <- ggplot(subset(ema_long, !is.na(day_of_week)), 
                                  aes(x = day_of_week, y = prop_drink_type_responses, 
                                    color = drink_type), group = drink_type) +
  geom_jitter(aes(group = drink_type, color = drink_type), alpha = .1) +
  stat_summary(aes(group = drink_type, color = drink_type), fun = mean, geom = "point", size = 6) +
  stat_summary(aes(group = drink_type, color = drink_type), fun = mean, geom = "line", size = 3) +
  scale_color_manual(values = alc_colors,name = "Drink Type")+
  theme_cowplot() +
    theme(
      axis.text.x = element_text(size = 16),
      axis.title.x = element_text(size = 18),
      axis.ticks.x = element_blank(),
      axis.text.y = element_text(size = 14),
      axis.title.y = element_text(size = 18)
    ) +
  scale_y_continuous(breaks = seq(0, 1, by = .25)) +
  labs(title = "", x = "Day of Week", y = "Choices for Alcohol (%)")
day_of_week_type_plot
```

```{r}
# ggsave("day_of_week_type_plot.jpeg", day_of_week_type_plot, device = "jpeg", width = 7,
#        height = 4, dpi = 300)
```

# Hourly Choices for Alcohol type Plot


```{r}
hourly_type_plot <- ggplot(subset(ema_long, hour >= 15 & hour < 23), 
                                  aes(x = hour, y = prop_drink_type_responses, 
                                      color = drink_type), group = drink_type) +
  geom_jitter(alpha = .1) +
  stat_summary(aes(group = drink_type), fun = mean, geom = "point", size = 6) +
  stat_summary(aes(group = drink_type), fun = mean, geom = "line", size = 3) +
  stat_summary(aes(group = drink_type), fun.data = mean_se, geom = "errorbar", 
               width = 0.2, color = "black") +
  scale_color_manual(values = alc_colors,name = "Drink Type")+
  theme_cowplot() +
    theme(
      axis.text.x = element_text(size = 16),
      axis.title.x = element_text(size = 18),
      axis.ticks.x = element_blank(),
      axis.text.y = element_text(size = 14),
      axis.title.y = element_text(size = 18)
    ) +
  scale_y_continuous(breaks = seq(0, 1, by = .25)) +
  labs(title = "", x = "Hour", y = "Choices for Alcohol (%)")
hourly_type_plot
```

```{r}
# ggsave("hourly_type_plot.jpeg", hourly_type_plot, device = "jpeg", width = 7,
#        height = 4, dpi = 300)
```

# Overall choices for alc by location

```{r}
plot_boxplot <- function(dat, xvar) {
  n_levels <- length(unique(pull(dat, {{xvar}})))
  purples <- colorRampPalette(c("#800870", "#b11ad6"))(n_levels)
  
  ggplot(dat,
  aes(x = {{xvar}}, y = prop_alc_responses, color = {{xvar}})) +
  geom_jitter(alpha = .05) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.15, color = "black") +
    scale_color_manual(values = purples, guide = "none") + 
  # geom_boxplot(outlier.shape = NA, alpha = 0.8, color = "black") +
  # scale_fill_manual(values = alc_colors, name = "Drink Type") +
  theme_cowplot() +
  theme(
    strip.text = element_text(size = 21, face = "bold"),
    axis.text.x = element_text(size = 10, angle = 45, hjust = 1),
    axis.text.y = element_text(size = 14),
    axis.title.y = element_text(size = 21),
    axis.title.x = element_text(size = 21))
}
loc_boxplot <- (plot_boxplot(subset(ema_long, !is.na(location)), location)) +
  labs(title = "",x = "Location",y = "Choices for Alcohol (%)")
loc_boxplot
```

# ICC for alc by location

```{r}
locations <- c("bar_club", "home", "other", "outdoors", "restaurant_cafe",
               "school_work", "someone_elses_home")
for (place in locations) {
  print(place)
  print(performance::icc(model_icc(subset(ema_lead, location == place), 
                                    prop_alc_responses ~ 1 + (1|subject))))
  cat('\n')
}
```


# Overall choices for alc by social context

```{r}
soc_boxplot <- (plot_boxplot(subset(ema_long, !is.na(social_context_overall)), 
                             social_context_overall)) +
  labs(title = "",x = "Social Context",y = "Choices for Alcohol (%)")
soc_boxplot
```

```{r}
contexts_overall_plot <- ggpubr::ggarrange(
  loc_boxplot, soc_boxplot,
  ncol = 2,
  nrow = 1,
  widths = c(1, 1),
  labels = c("A", "B"),
  font.label = list(size = 18, face = "bold"), # Optional formatting
  label.x = 0,
  label.y = 1
)
ggsave("contexts_overall_plot.jpeg", contexts_overall_plot, device = "jpeg", width = 16, height = 5, dpi = 300)
```

# Choices for alc type by location

```{r}
ema_long$drink_type <- factor(
  ema_long$drink_type,
  levels = c("prop_liquor_responses", "prop_wine_responses", 
             "prop_beer_responses", "prop_seltzer_responses"),
  labels = c("Liquor", "Wine", "Beer", "Seltzer"))

ema_long$location <- factor(ema_long$location,
  levels = c("home", "school_work", "someone_elses_home", "outdoors", "restaurant_cafe",
             "bar_club", "other"),
  labels = c("Home", "School/Work", "Other's Home", "Outdoors", "Restaurant",
             "Bar/Club", "Other"))
```

```{r}
loc_type_boxplot <- ggplot(ema_long %>% filter(!is.na(location)),
  aes(x = drink_type, y = prop_drink_type_responses, fill = drink_type)) +
  geom_jitter(aes(color = drink_type), alpha = .1) + 
  geom_boxplot(aes(fill = drink_type), outlier.shape = NA, alpha = 0.2, color = "black") +
  # stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5, color = "black") +
  facet_wrap(~location, nrow = 1, scales = "free_x") +
  scale_color_manual(values = alc_colors, name = "Drink Type") +
  scale_fill_manual(values = alc_colors, name = "Drink Type") +
  theme_cowplot() +
    guides(fill = guide_legend(override.aes = list(alpha = 1))) +
  labs(title = "",x = "Location",y = "Choices for Alcohol (%)") +
  theme(
    legend.position = "right",
    strip.text = element_text(size = 21, face = "bold"),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 14),
    axis.title.y = element_text(size = 21),
    axis.title.x = element_text(size = 21))

loc_type_boxplot
```

```{r}
ggsave("loc_type_boxplot.jpeg", loc_type_boxplot, device = "jpeg", width = 16, height = 5, dpi = 300)
```

# location descriptive statistics

```{r}
ema_lead %>%
  filter(!is.na(prop_alc_responses)) %>%
  group_by(location) %>%
  summarise(mean_choices = mean(prop_alc_responses, na.rm = T),
            sd_choices = sd(prop_alc_responses, na.rm = T),
            min_choices = min(prop_alc_responses, na.rm = T),
            max_choices = max(prop_alc_responses, na.rm = T))
```

# Correlations between choices for drink types and drinking behavior

```{r}
ema_lead %>%
  ungroup() %>%
  summarise(
     liquor_intend_cor = cor(ema_lead$alc_intend, ema_lead$prop_liquor_responses, 
                      use = "complete.obs"),
     liquor_consume_cor = cor(ema_lead$alc_consumed_today, ema_lead$prop_liquor_responses, 
                       use = "complete.obs"),
     
     wine_intend_cor = cor(ema_lead$alc_intend, ema_lead$prop_wine_responses, 
                      use = "complete.obs"),
     wine_consume_cor = cor(ema_lead$alc_consumed_today, ema_lead$prop_wine_responses, 
                       use = "complete.obs"),
     
     beer_intend_cor = cor(ema_lead$alc_intend, ema_lead$prop_beer_responses, 
                      use = "complete.obs"),
     beer_consume_cor = cor(ema_lead$alc_consumed_today, ema_lead$prop_beer_responses, 
                       use = "complete.obs"),
     
     seltzer_intend_cor = cor(ema_lead$alc_intend, ema_lead$prop_seltzer_responses, 
                      use = "complete.obs"),
     seltzer_consume_cor = cor(ema_lead$alc_consumed_today, ema_lead$prop_seltzer_responses, 
                       use = "complete.obs")
  )
```


# Drink Type by Social Context Boxplot

```{r}
ema_long$social_context_overall <- factor(ema_long$social_context_overall,
  levels = c("alone", "romantic_partner", "family", "friend_roommate", "coworker_classmate",
             "stranger", "multiple", "other"),
  labels = c("Alone", "Romantic Partner", "Family", "Friend/Roommate", "Coworker/Classmate",
             "Stranger","Multiple", "Other"))
```


```{r}
soc_type_boxplot <- ggplot(ema_long %>% filter(!is.na(social_context_overall) &
                                                 social_context_overall != "Other"),
  aes(x = drink_type, y = prop_drink_type_responses, fill = drink_type)) +
  geom_jitter(aes(color = drink_type), alpha = .1) + 
  geom_boxplot(aes(fill = drink_type), outlier.shape = NA, alpha = 0.2, color = "black") +
  # stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5, color = "black") +
  facet_wrap(~social_context_overall, nrow = 1, scales = "free_x") +
  scale_color_manual(values = alc_colors, name = "Drink Type") +
  scale_fill_manual(values = alc_colors, name = "Drink Type") +
  theme_cowplot() +
  guides(fill = guide_legend(override.aes = list(alpha = 1))) +
  labs(title = "",x = "Social Context",y = "Choices for Alcohol (%)") +
  theme(
    legend.position = "right",
    strip.text = element_text(size = 14, face = "bold"),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 14),
    axis.title.y = element_text(size = 21),
    axis.title.x = element_text(size = 21))

soc_type_boxplot
```

```{r}
ggsave("soc_type_boxplot.jpeg", soc_type_boxplot, device = "jpeg", width = 16, height = 5, dpi = 300)
```

# Combine Drink type context box plots

```{r}
contexts_type_plot <- ggpubr::ggarrange(
  loc_type_boxplot, soc_type_boxplot,
  ncol = 1,
  nrow = 2,
  heights = c(1, 1),
  labels = c("A", "B"),
  font.label = list(size = 18, face = "bold"), # Optional formatting
  label.x = 0,
  label.y = 1
)
ggsave("contexts_type_plot.jpeg", contexts_type_plot, device = "jpeg", width = 16, height = 10, dpi = 300)
```


# Proportion statistics for contexts

```{r}
ema_lead %>%
  ungroup() %>%
  summarise(alone_prop = sum(social_context_overall == "alone", na.rm = T)/
              sum(!is.na(social_context_overall)),
            home_prop = sum(location == "home", na.rm = T)/
              sum(!is.na(location)))
```


# heat map for location and social context

```{r}
heatmap_data <- ema_lead %>%
  ungroup() %>%
  filter(!is.na(location), !is.na(social_context_overall)) %>%
  mutate(
  soc_binary = ifelse(social_context_overall == "alone", "Alone", "Not Alone"),
  loc_binary = ifelse(location == "home", "Home", "Not at Home")
  ) %>%
  group_by(loc_binary, soc_binary) %>%
  summarise(
    prop_alc = round(mean(prop_alc_responses, na.rm = T), 3),
    n_obs = n()
  )

# Step 2: Create heatmap with text labels
soc_loc_heatmap <- ggplot(heatmap_data, aes(x = loc_binary, y = soc_binary, fill = prop_alc)) +
  geom_tile(color = "white") +
  geom_text(aes(label = prop_alc), size = 4) +
  scale_fill_gradient(
    low = "#f0f0f0", high = "#5c677d", na.value = "grey90",
    name = "Choices for\nAlcohol (%)",
    limit = c(.3, .4)
  ) +
  labs(x = "Location", y = "Social Context", title = "Alcohol Choice Proportions") +
  theme_cowplot() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
soc_loc_heatmap
```

```{r}
ggsave("soc_loc_heatmap.jpeg", soc_loc_heatmap, device = "jpeg", width = 7, height = 5, dpi = 300)
```


# plot drink type by alc cue

```{r}
cue_type_plot <- facet_line_plot(subset(ema_long, !is.na(alc_cue)), alc_cue, alc_colors)
cue_type_plot
```



