---
title: "k99_data_plots"
author: "Gavin Kelly"
date: "2025-06-06"
output: html_document
---

This is a script for the data plots for the k99.2 EMA study.

# Description of Plots

  *With extra things to know about each*

Figure 1 (line 158): This plots race (barplot), audit scores(raincloud plot), 
age (raincloud plot), and drinking motives (histogram-raincloud plot) from the baseline data.

  I create a raincloud plot function here that I use throughout the rest of the script.

Figure 2 (line 371): This is a heatmap of the correlations of important study variables
within each participant. It plots average emotions from EMA assessments. The 6 variables
of interest from the 2AFC: choices for alcohol (%), median response times,
and DDM parameters from the 2AFC sessions. These are also averaged for each
participant. It also plots drinking motives from the baseline.
  
  This loosely follows this tutorial.
  https://www.geeksforgeeks.org/create-heatmap-in-r-using-ggplot2/
  upper.tri deletes the top half of the correlation matrix.

Figure 3 (line 493): This is a plot ranking the baseline ratings of alcoholic and 
non-alcoholic drinks using SEM bars with jittered points behind. This section 
includes two plot options, one with brand names and one with generic names.

  This one just has a lot of formatting and renaming drinks.

Figure 4 (line 788): This combines a barplot of stress event (yes/no), a bar plot
of type of stress event, and a histogram-raincloud plot of stress intensity ratings.

Figure 5 (line 923): This creates histogram-raincloud plots for the three emotions 
from the EMA assessments (Stress, NA, and PA).

  I use fct_relevel here to avoid using facet_wrap.

Figure 6 (line 983): This figure combines raincloud plots of the 6 variables of 
interest from the 2AFC.

Figure 7 (line 1091): The figure plots the relationship between the value function
and the choices for alcohol (%) and median rt. This plots the data by SESSION,
so each data point is one session from one participant.

  I create a plot_value function here that uses group = interaction to ensure 
  there is one data point for each subject session combination.

Figure 8 (line 1179): This plots the 6 variables of interest by stress event (yes/no). 
The points for each session are jittered behind.

Figure 9 (line 1299): This creates 3 figures actually, one for each emotion (stress, NA, PA).
Each figure plots the relationship between emotions from assessments and the
6 variables of interest.

Figure 10 (line 1596): This plots the number of each responses for each day in the 
EMA period, measured by days since the baseline was completed.

  I create a new df here with the desired variables, and update sessions 1, 2, 3
  based on the number of completions they had that day.

# Other things to know about the code:

I have commented out user-specific code like working directory, loading data,
and saving the plots using ggsave.

Feel free to save individual plots using ggsave rather than the combined figures.

Each plot should print when the code is run, but some will look weird before they
are reformatted and saved to files. The formatting in the commented code is good.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("C:/Users/gavin/OneDrive - andrew.cmu.edu/Documents/RADLab")
```

## Load Packages

```{r}
library(dplyr)
library(lubridate)
library(ggplot2)
library(tidyr)
library(psych)
library(ggrain)
library(gghalves)
library(ggdist)
library(ggridges)
library(forcats)
library(reshape2)
library(cowplot)
library(ggpubr)
```


## Loading Data

```{r}
# k99_shared_data <- read.csv("k99_shared_data.csv")
```

We can create data frames on the baseline and EMA assessment level.

```{r}
baseline_data_processed <- k99_shared_data %>%
  group_by(subject) %>%
  slice(1) %>%
  ungroup()
  
survey_data_processed %>% 
  group_by(subject, session) %>%
  slice(1) %>%
  ungroup()
```







## Figure 1: Descriptive Statistics

We can make a raincloud plot of the audit scores.

First we write a function for the raincloud plot. 

```{r}
plot_rc <- function(df, xvar, hex_code, adj, ht1, just, nudge, alp, sz, ht2) {
  ggplot(df, aes(x = xvar, y = "", fill = hex_code, color = hex_code)) +
  ggdist::stat_halfeye(point_colour = NA,
                         adjust = adj,
                         width = .5,
                          height = ht1,
                         .width = 0,            
                         justification = just) +
  geom_boxplot(width = .1, alpha = .5, lwd = 1, fatten = 1.5, outlier.shape = NA,
                          size = 1.15, position = position_nudge(y = nudge)) +
  geom_jitter(aes(color = hex_code), alpha = alp, size = sz, height = ht2) +
  coord_flip() +
  theme_cowplot() +
  scale_fill_manual(values = hex_code) +
  scale_color_manual(values = hex_code) +
    theme(
      legend.position = "none",
      axis.text.x = element_text(size = 18),
      axis.title.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.text.y = element_text(size = 14),
      axis.title.y = element_text(size = 18)
    ) +
  scale_x_continuous()
}
```

```{r}
audit_raincloud_plot <- plot_rc(baseline_data_processed, baseline_data_processed$audit_score, "black",
                                .6, .5, -.6, -.22, .15, .8, .05)
audit_raincloud_plot + labs(title = "", x = "Audit Score", y = "") + 
  scale_x_continuous(breaks = seq(0, 40, by = 5))
```


We can also make raincloud plots of the drinking motives variables. For this,
we need to pivot longer, creating one variable for all the motives.

The conformity motives are extremely one-inflated, so we will randomize some of these
values to be between 1 and 1.1.

```{r}
motives_items <- c("dmq_social", "dmq_enhancement", "dmq_coping", "dmq_conformity")
baseline_long_mot <- pivot_longer(baseline_data_processed, cols = all_of(motives_items),
                              names_to = "motive", values_to = "score")
baseline_long_mot <- baseline_long_mot %>%
  mutate(
    motive = case_when(
      motive == "dmq_social" ~ "Social Motives",
      motive == "dmq_enhancement" ~ "Enhancement Motives",
      motive == "dmq_coping" ~ "Coping Motives",
      motive == "dmq_conformity" ~ "Conformity Motives"
    )
  )
```


```{r}
colors <- c("#2C6E49", "#52796f", "#68a691", "#77ba8b")
motives_raincloud_plot <- ggplot(baseline_long_mot, aes(x = score, y = motive,
                                                        fill = motive, color = motive)) +
  facet_wrap(~ fct_rev(motive), scales = "free_x", nrow = 1) +
  ggridges::stat_binline(bins = 5, breaks = c(.95, 1.77, 2.59, 3.41, 4.23, 5.05), 
                         scale = 0.3, alpha = 0.5, lwd = 1, fatten = 1.5,
                         position = position_nudge(y = 0.15), draw_baseline = F, pad = F) +
  geom_boxplot(width = .1, alpha = .5, lwd = 1, fatten = 1.5, outlier.shape = NA,
                          size = 1.15, position = position_nudge(y = -0.22)) +
  geom_jitter(aes(color = motive), alpha = 0.3, size = 0.8, height = 0.05) +
  coord_flip() +
  theme_cowplot() +
  scale_fill_manual(values = colors) +
  scale_color_manual(values = colors) +
    theme(
      strip.text = element_text(size = 18, face = "bold"),
      legend.position = "none",
      axis.text.x = element_blank(),
      axis.title.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.text.y = element_text(size = 14),
      axis.title.y = element_text(size = 18)
    ) +
  labs(title = "", x = "DMQ Score", y = "") +
  scale_x_continuous(breaks = seq(1, 5, by = 1))
motives_raincloud_plot
```

We can also make a raincloud plot for the age scores.

```{r}
age_raincloud_plot <- plot_rc(baseline_data_processed, baseline_data_processed$age, "#1d5234",
                                .6, .5, -.6, -.22, .15, .8, .05)
age_raincloud_plot + labs(title = "", x = "Age", y = "") + 
  scale_x_continuous(breaks = c(21, 30, 40, 50, 60, 70, 80))
```

We can now make some bar charts for the categorical demographic variables.

I would like put race, gender, and sexuality on one plot, sorted by frequency.

```{r}
demographic_items <- c("race", "gender", "sexuality")
baseline_long_demo <- pivot_longer(baseline_data_processed, cols = all_of(demographic_items),
                              names_to = "demographic", values_to = "response")

baseline_long_demo <- baseline_long_demo %>%
  mutate(
    response = case_when(
      response == "straight" ~ "Straight",
      response == "white" ~ "White",
      response == "woman" ~ "Woman",
      response == "man" ~ "Man",
      (response == "multiple" & demographic == "sexuality") ~ "LGBQ+",
      (response == "multiple" & demographic == "gender") ~ "Other",
      (response == "multiple" & demographic == "race") ~ "Other/Multiple",
      response == "bisexual" ~ "LGBQ+",
      response == "african_american" ~ "Black/African American",
      response == "gay" ~ "LGBQ+",
      response == "hispanic" ~ "Hispanic/Latinx",
      response == "southeast_asian" ~ "Asian",
      response == "east_asian" ~ "Asian",
      response == "pansexual" ~ "LGBQ+",
      response == "south_asian" ~ "Asian",
      response == "agender" ~ "Other",
      response == "asexual" ~ "LGBQ+",
      response == "lesbian" ~ "LGBQ+",
      response == "queer" ~ "LGBQ+",
      response == "trans_woman" ~ "Other",
      TRUE ~ response
    )
  )
baseline_long_demo <- baseline_long_demo %>%
  mutate(
    demographic = case_when(
      demographic == "race" ~ "Race/Ethnicity",
      demographic == "gender" ~ "Gender",
      demographic == "sexuality" ~ "Sexuality",
    )
  )
desired_order <- c("Woman", "Man", "Other",
  "Asian", "Black/African American", "White", "Other/Multiple", "Hispanic/Latinx",
  "Straight", "LGBQ+")
baseline_long_demo <- baseline_long_demo %>%
  mutate(response = factor(response, levels = desired_order))
```


```{r}
colors <- c("#709775", "#415d43", "#8fb996")
demographics_barplot <- ggplot(baseline_long_demo, aes(x = response, group = demographic,
                                                fill = demographic, color = demographic)) +
  geom_bar() +
  facet_wrap(~demographic, scales = "free_x", nrow = 1) +
  theme_cowplot() +
  scale_fill_manual(values = colors) +
  scale_color_manual(values = colors) +
    theme(
      legend.position = "none",
      strip.text = element_text(size = 21, face = "bold"),
      axis.text.x = element_text(
          angle = 45, 
          vjust = 1, 
          hjust = 1, 
          size = 16),
      axis.title.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.text.y = element_text(size = 14),
      axis.title.y = element_text(size = 21)
    ) +
    ylim(0, 210) +
    scale_y_continuous(expand = expansion(mult = c(0, 0.05))) +
  labs(title = "", x = "Demographic", y = "Count")
demographics_barplot
```





Now we can save all of the demographic plots together using ggarrange.

```{r}
# figure1 <- ggpubr::ggarrange(
#   age_raincloud_plot, demographics_barplot, audit_raincloud_plot, motives_raincloud_plot,
#   ncol = 2, 
#   nrow = 2,
#   widths = c(1, 3),
#   labels = c("A", "B", "C", "D"),
#   font.label = list(size = 22, face = "bold"), # Optional formatting
#   label.x = 0,
#   label.y = 1 
# )
# figure1
# ggsave("figure1.jpg", figure1, width = 18, height = 15, dpi = 300)
```












## Figure 2: Heat Map of Participant Characteristics

We need to make a new DF with only our target variables

  baseline scales: audit & dmq scores
  ema vals: mean stress, na, pa state, prop of choices for alcohol, median rt

First we calculate the means for participant characteristics in the EMA surveys.

```{r}
k99_shared_data_2 <- k99_shared_data %>%
  group_by(subject, session) %>%
  mutate(
    mean_prop_alc_responses = sum(response == "alc", na.rm = T) / 
      (sum(response == "alc", na.rm = T) + sum(response == "soft", na.rm = T)),
    mean_median_rt = median(rt, na.rm = T)
  ) %>%
    slice(1) %>%
  ungroup()
k99_shared_data_2 <- k99_shared_data_2 %>%
  group_by(subject) %>%
  mutate(
    mean_stress_state = mean(stress_state, na.rm = T),
    mean_NA_state = mean(NA_state, na.rm = T),
    mean_PA_state = mean(PA_state, na.rm = T),
    mean_prop_alc_responses = mean(mean_prop_alc_responses),
    mean_median_rt = mean(mean_median_rt)
  ) %>%
  slice(1)
```

Now we add these variables along with the baseline variables into a new df.

```{r}
cor_df <- k99_shared_data_2[c("mean_stress_state", "mean_NA_state", "mean_PA_state",
                            "mean_prop_alc_responses", "mean_median_rt", 
                            "B", "drift", "alcbias", "nondectime", "audit_score",
                            "dmq_social", "dmq_enhancement", "dmq_coping", "dmq_conformity")]
head(cor_df)
cor_df <- rename(cor_df, "Average Stress" = mean_stress_state)
cor_df <- rename(cor_df, "Average Negative Affect" = mean_NA_state)
cor_df <- rename(cor_df, "Average Positive Affect" = mean_PA_state)
cor_df <- rename(cor_df, "Avg. Choices for Alcohol (%)" = mean_prop_alc_responses)
cor_df <- rename(cor_df, "Median Response Time" = mean_median_rt)

cor_df <- rename(cor_df, "Drift Rate" = drift)
cor_df <- rename(cor_df, "Alcohol Bias" = alcbias)
cor_df <- rename(cor_df, "Decision Boundary" = B)
cor_df <- rename(cor_df, "Non-Decision Time" = nondectime)

cor_df <- rename(cor_df, "Audit Score" = audit_score)
cor_df <- rename(cor_df, "Social Motives" = dmq_social)
cor_df <- rename(cor_df, "Coping Motives" = dmq_coping)
cor_df <- rename(cor_df, "Enhancement Motives" = dmq_enhancement)
cor_df <- rename(cor_df, "Conformity Motives" = dmq_conformity)

#cor_df <- distinct(cor_df)
head(cor_df)
#cor_matrix <- cor(cor_df[sapply(cor_df, is.numeric)])
cor_matrix <- cor_df %>%
  cor(use = "pairwise.complete.obs") %>% 
  round(., 2)
cor_matrix[upper.tri(cor_matrix)] <- NA
cor_matrix <- melt(cor_matrix, na.rm = T)
```

Now we plot the correlations.

```{r}
cor_plot <- ggplot(cor_matrix, aes(x = Var1, y = Var2, fill = value)) + 
  geom_tile(color = "white") + 
  geom_text(aes(Var1, Var2, label = value), color = "black", size = 6) +
  scale_fill_gradient2(low = "#E66101", 
                       high = "#2166AC", 
                       mid = "white", 
                       midpoint = 0, 
                       limit = c(-1, 1), 
                       space = "Lab", 
                       name = "Pearson correlation") + 
  theme_cowplot() + 
    theme(panel.grid.major = element_blank(), 
        panel.background = element_blank(), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(), 
        panel.border = element_blank(), 
        axis.ticks = element_blank(), 
        axis.text.x = element_text(
          angle = 45, 
          vjust = 1, 
          hjust = 1, 
          size = 18), 
        axis.text.y = element_text(size = 18), 
        #legend.justification = c(1,0), 
        #legend.position = c(0.3, 0.65), 
        legend.direction = "vertical", 
        legend.key.size = unit(1, 'cm'),
        legend.text = element_text(size = 14), 
        legend.title = element_text(size = 30) + 
  guides(fill = guide_colorbar(barwidth = 7, barheight = 1, 
                               title.position = "top", title.hjust = 0.5))) + 
  coord_fixed()
```

Save the plot to files.

```{r}
# ggsave("correlation_matrix.jpeg", cor_plot, device = "jpeg", width = 15, height = 12.5, dpi = 300)
```













## Figure 3: distribution of drink ratings

```{r}
drink_vals <- c("alc01", "alc02", "alc03", "alc04", "alc05", 
              "alc06", "alc07", "alc08", "alc09", "alc10", 
              "alc11", "alc12", "alc13", "alc14", "alc15", 
              "alc16", "alc17", "alc18", "alc19", "alc20", 
              "alc21", "alc22", "alc23", "alc24", "alc25",
              "alc26", "alc27", "alc28", "alc29", "alc30",
              "soft01", "soft02", "soft03", "soft04", "soft05", 
              "soft06", "soft07", "soft08", "soft09", "soft10", 
              "soft11", "soft12", "soft13", "soft14", "soft15", 
              "soft16", "soft17", "soft18", "soft19", "soft20", 
              "soft21", "soft22", "soft23", "soft24", "soft25",
              "soft26", "soft27", "soft28", "soft29", "soft30")
baseline_long <- pivot_longer(baseline_data_processed, cols = all_of(drink_vals), 
                              names_to = "drink", values_to = "rating")
```

```{r}
non_alcoholic <- c("soft01", "soft02", "soft03", "soft04", "soft05", 
              "soft06", "soft07", "soft08", "soft09", "soft10", 
              "soft11", "soft12", "soft13", "soft14", "soft15", 
              "soft16", "soft17", "soft18", "soft19", "soft20", 
              "soft21", "soft22", "soft23", "soft24", "soft25",
              "soft26", "soft27", "soft28", "soft29", "soft30")
baseline_long$alcoholic = "none"
baseline_long <- baseline_long %>%
  mutate(
    alcoholic = case_when(
      drink %in% non_alcoholic ~ "Non-Alcoholic Drinks",
      TRUE ~ "Alcoholic Drinks"
    )
  )
```

```{r}
baseline_long$drink_name = "none"
baseline_long <- baseline_long %>%
  mutate(
    drink_name = case_when(
      drink == "alc01" ~ "Budweiser",
      drink == "alc02" ~ "Bud Light",
      drink == "alc03" ~ "Coors Light",
      drink == "alc04" ~ "Corona",
      drink == "alc05" ~ "Miller Lite",
      drink == "alc06" ~ "Michelob Ultra",
      drink == "alc07" ~ "Stone IPA",
      drink == "alc08" ~ "Voodoo IPA",
      drink == "alc09" ~ "White Claw (berry)",
      drink == "alc10" ~ "White Claw (mango)",
      drink == "alc11" ~ "Truly (berry)",
      drink == "alc12" ~ "Truly (pineapple)",
      drink == "alc13" ~ "Sauvignon Blanc NZ",
      drink == "alc14" ~ "Sauvignon Blanc CA",
      drink == "alc15" ~ "Cabernet CA",
      drink == "alc16" ~ "Cabernet CA 2",
      drink == "alc17" ~ "Sparkling Wine",
      drink == "alc18" ~ "Absolut",
      drink == "alc19" ~ "Tito's",
      drink == "alc20" ~ "Smirnoff",
      drink == "alc21" ~ "1800",
      drink == "alc22" ~ "Cuervo Silver",
      drink == "alc23" ~ "Cuervo Gold",
      drink == "alc24" ~ "Tanqueray Gin",
      drink == "alc25" ~ "Gordon's Gin",
      drink == "alc26" ~ "Jim Beam",
      drink == "alc27" ~ "Jack Daniels",
      drink == "alc28" ~ "Jameson",
      drink == "alc29" ~ "Captain Morgan",
      drink == "alc30" ~ "Bacardi"
    )
  )
```


```{r}
baseline_long <- baseline_long %>%
  mutate(
    drink_name = case_when(
      drink == "soft01" ~ "Coke",
      drink == "soft02" ~ "Diet Coke",
      drink == "soft03" ~ "Coke Zero",
      drink == "soft04" ~ "Pepsi",
      drink == "soft05" ~ "Diet Pepsi",
      drink == "soft06" ~ "Pepsi Zero",
      drink == "soft07" ~ "Dr Pepper",
      drink == "soft08" ~ "Diet Dr Pepper",
      drink == "soft09" ~ "Sprite",
      drink == "soft10" ~ "7up",
      drink == "soft11" ~ "Sunkist",
      drink == "soft12" ~ "Mtn Dew",
      drink == "soft13" ~ "Canada Dry",
      drink == "soft14" ~ "Root Beer",
      drink == "soft15" ~ "Arizona (green)",
      drink == "soft16" ~ "Arizona (red)",
      drink == "soft17" ~ "Snapple",
      drink == "soft18" ~ "Gatorade (orange)",
      drink == "soft19" ~ "Gatorade (red)",
      drink == "soft20" ~ "Monster",
      drink == "soft21" ~ "Diet Monster",
      drink == "soft22" ~ "Redbull",
      drink == "soft23" ~ "Diet Redbull",
      drink == "soft24" ~ "Celsius (lime)",
      drink == "soft25" ~ "Celsius (orange)",
      drink == "soft26" ~ "Strawberry Smoothie",
      drink == "soft27" ~ "Mango Smoothie",
      drink == "soft28" ~ "Orange Juice",
      drink == "soft29" ~ "Coffee",
      drink == "soft30" ~ "Frappuccino",
      TRUE ~ drink_name
    )
  )
```



```{r}
baseline_long <- baseline_long %>%
  group_by(drink_name) %>%
  mutate(mean_rating = mean(rating, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(drink_name = reorder(drink_name, mean_rating))
```

```{r}
drink_colors <- colorRampPalette(c(
  "#B2182B",  # muted red
  "#D6604D",  # soft orange
  "#66BB66",  # desaturated green
  "#4393C3",  # muted blue
  "#762A83"   # muted purple
))(30)
```

```{r}
library(cowplot)

# Shared plotting function
plot_by_type <- function(data, title) {
  ggplot(data, aes(x = drink_name, y = rating, color = drink_name)) +
    geom_jitter(size = 0.35, alpha = 0.3, width = 0.2) + 
    stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5, color = "black") +
    scale_color_manual(values = drink_colors) + 
    labs(title = title, y = "Rating of Drink", x = NULL, color = "Drink") +
    coord_cartesian(ylim = c(1, 4)) +
    theme_minimal(base_size = 13) +
    guides(color = guide_legend(
    override.aes = list(size = 4),
    ncol = 2,
    byrow = F
  )) +
    theme_cowplot() +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      plot.title = element_text(size = 14.5, face = "bold", hjust = 0.5),
      axis.text.y = element_text(size = 14),
      axis.title.y = element_text(size = 14),
      legend.title = element_text(size = 17),
      legend.text = element_text(size = 14.5),
      legend.key.height = unit(0.3, "cm")
    )
}

# Generate plots
plot_alc <- plot_by_type(filter(baseline_long, alcoholic == "Alcoholic Drinks"), "Alcoholic Drinks")
plot_nonalc <- plot_by_type(filter(baseline_long, alcoholic == "Non-Alcoholic Drinks"), "Non-Alcoholic Drinks")

# Combine vertically
final_plot <- plot_grid(plot_alc, plot_nonalc, ncol = 1, align = "v")
final_plot
```

Save the plot to files.

```{r}
# ggsave("faceted_drink_plot.jpeg", final_plot, device = "jpeg", width = 12, height = 10, dpi = 300)
```


Now we will make a plot with non-copyrite names, ordered alphabetically.

```{r}
baseline_long <- baseline_long %>%
  mutate(
    drink_name = case_when(
      drink_name == "Bud Light" ~ "Beer 1",
      drink_name == "Budweiser" ~ "Beer 2",
      drink_name == "Coors Light" ~ "Beer 3",
      drink_name == "Corona" ~ "Beer 4",
      drink_name == "Michelob Ultra" ~ "Beer 5",
      drink_name == "Miller Lite" ~ "Beer 6",
      drink_name == "Stone IPA" ~ "IPA 1",
      drink_name == "Voodoo IPA" ~ "IPA 2",
      drink_name == "Truly (berry)" ~ "Seltzer 1",
      drink_name == "Truly (pineapple)" ~ "Seltzer 2",
      drink_name == "White Claw (berry)" ~ "Seltzer 3",
      drink_name == "White Claw (mango)" ~ "Seltzer 4",
      drink_name == "Sauvignon Blanc CA" ~ "White Wine 1",
      drink_name == "Sauvignon Blanc NZ" ~ "White Wine 2",
      drink_name == "Cabernet CA" ~ "Red Wine 1",
      drink_name == "Cabernet CA 2" ~ "Red Wine 2",
      drink_name == "Sparkling Wine" ~ "Sparkling Wine",
      drink_name == "Absolut" ~ "Vodka 1",
      drink_name == "Smirnoff" ~ "Vodka 2",
      drink_name == "Tito's" ~ "Vodka 3",
      drink_name == "1800" ~ "Tequila 1",
      drink_name == "Cuervo Gold" ~ "Tequila 2",
      drink_name == "Cuervo Silver" ~ "Tequila 3",
      drink_name == "Gordon's Gin" ~ "Gin 1",
      drink_name == "Tanqueray Gin" ~ "Gin 2",
      drink_name == "Jim Beam" ~ "Bourbon",
      drink_name == "Jack Daniels" ~ "Whiskey 1",
      drink_name == "Jameson" ~ "Whiskey 2",
      drink_name == "Bacardi" ~ "Rum 1",
      drink_name == "Captain Morgan" ~ "Rum 2",
      TRUE ~ drink_name
    )
  )
```


```{r}
baseline_long <- baseline_long %>%
  mutate(
    drink_name = case_when(
      drink_name == "7up" ~ "Soda 1",
      drink_name == "Canada Dry" ~ "Soda 2",
      drink_name == "Coke" ~ "Soda 3",
      drink_name == "Coke Zero" ~ "Soda 4",
      drink_name == "Diet Coke" ~ "Soda 5",
      drink_name == "Diet Dr Pepper" ~ "Soda 6",
      drink_name == "Diet Pepsi" ~ "Soda 7",
      drink_name == "Dr Pepper" ~ "Soda 8",
      drink_name == "Mtn Dew" ~ "Soda 9",
      drink_name == "Pepsi" ~ "Soda 10",
      drink_name == "Pepsi Zero" ~ "Soda 11",
      drink_name == "Root Beer" ~ "Soda 12",
      drink_name == "Sprite" ~ "Soda 13",
      drink_name == "Sunkist" ~ "Soda 14",
      drink_name == "Arizona (green)" ~ "Sweet Tea 1",
      drink_name == "Arizona (red)" ~ "Sweet Tea 2",
      drink_name == "Snapple" ~ "Sweet Tea 3",
      drink_name == "Gatorade (orange)" ~ "Sports Drink 1",
      drink_name == "Gatorade (red)" ~ "Sports Drink 2",
      drink_name == "Celsius (lime)" ~ "Energy Drink 1",
      drink_name == "Celsius (orange)" ~ "Energy Drink 2",
      drink_name == "Diet Monster" ~ "Energy Drink 3",
      drink_name == "Diet Redbull" ~ "Energy Drink 4",
      drink_name == "Monster" ~ "Energy Drink 5",
      drink_name == "Redbull" ~ "Energy Drink 6",
      drink_name == "Mango Smoothie" ~ "Smoothie 1",
      drink_name == "Strawberry Smoothie" ~ "Smoothie 2",
      drink_name == "Orange Juice" ~ "Orange Juice",
      drink_name == "Coffee" ~ "Coffee 1",
      drink_name == "Frappuccino" ~ "Coffee 2",
      TRUE ~ drink_name
    )
  )
```

```{r}
baseline_long <- baseline_long %>%
  group_by(drink_name) %>%
  mutate(mean_rating = mean(rating, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(drink_name = reorder(drink_name, mean_rating))
```


Now we plot the nondescript data.

```{r}
# Generate plots
plot_alc_nondescript <- plot_by_type(filter(baseline_long, alcoholic == "Alcoholic Drinks"), "Alcoholic Drinks")
plot_nonalc_nondescript <- plot_by_type(filter(baseline_long, alcoholic == "Non-Alcoholic Drinks"), "Non-Alcoholic Drinks")

# Combine vertically
final_plot_nondescript <- plot_grid(plot_alc_nondescript, plot_nonalc_nondescript, ncol = 1, align = "v")
final_plot_nondescript
```

```{r}
# ggsave("nondescript_drink_plot.jpeg", final_plot_nondescript, device = "jpeg", 
#width = 12, height = 10, dpi = 300)
```











## Figure 4: Descriptives for Stress Event Data

We will make 3 plots for stress event data: frequency of occurrence, type of event,
and stress ratings for events.

```{r}
event_freq_barplot <- ggplot(survey_data_processed, aes(x = stress_event,
                                                fill = "#fc8eac", color = "#fc8eac")) +
  geom_bar() +
  theme_cowplot() +
  scale_fill_manual(values = "#fc8eac") +
  scale_color_manual(values = "#fc8eac") +
    theme(
      legend.position = "none",
      axis.text.x = element_text(size = 16),
      axis.title.x = element_text(size = 18),
      axis.ticks.x = element_blank(),
      axis.text.y = element_text(size = 14),
      axis.title.y = element_text(size = 18)
    ) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05))) +
  labs(title = "", x = "Stress Event Occurred", y = "Count")
event_freq_barplot
```

```{r}
survey_data_event <- survey_data_processed %>%
  mutate(
    stress_event_type_overall = case_when(
      stress_event_type_overall == "argument" ~ "Argument",
      stress_event_type_overall == "difficulty_home" ~ "Home Difficulty",
      stress_event_type_overall == "difficulty_work_school" ~ "Work/School Difficulty",
      stress_event_type_overall == "health_issue" ~ "Health Issue",
      stress_event_type_overall == "multiple" ~ "Multiple",
      stress_event_type_overall == "neg_event_to_others" ~ "Witnessed Neg. Event",
      stress_event_type_overall == "other" ~ "Other",
      stress_event_type_overall == "social_dissapointment" ~ "Social Dissapointment"
    )
  )
# survey_data_event <- rename(survey_data_event, "Event Type" = "stress_event_type_overall")
pink_gradient <- c(
  "#fde3eb",  # lightest
  "#f8b5c7",
  "#f288a3",
  "#ec5a8b",
  "#E75480",  # middle
  "#d04074",
  "#b53066",
  "#951e55"   # darkest
)

stressor_order <- c("Argument", "Social Dissapointment", "Work/School Difficulty",
  "Home Difficulty", "Health Issue", "Witnessed Neg. Event", "Multiple", "Other")
survey_data_event <- survey_data_event %>%
  mutate(stress_event_type_overall = factor(stress_event_type_overall, levels = stressor_order))

event_type_barplot <- ggplot(data = subset(survey_data_event, !is.na(stress_event_type_overall)), 
                                           aes(x = stress_event_type_overall,
                                           fill = stress_event_type_overall, color = stress_event_type_overall)) +
  geom_bar() +
  theme_cowplot() +
  scale_fill_manual(values = pink_gradient) +
  scale_color_manual(values = pink_gradient) +
  guides(fill = guide_legend(direction = "vertical", ncol = 1)) +
  scale_x_discrete(labels = rep(" ", 8)) +
    theme(
      legend.title = element_blank(),
      axis.text.x = element_blank(),
      legend.text = element_text(size = 11), 
      axis.title.x = element_text(size = 18),
      axis.ticks.x = element_blank(),
      axis.text.y = element_text(size = 14),
      axis.title.y = element_text(size = 18),
      axis.text.x.bottom = element_text(margin = margin(t = 8))
      ) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05))) +
  labs(title = "", x = "Stress Event Type", y = "Count")
event_type_barplot 
```


```{r}
stress_level_plot <- ggplot(data = subset(survey_data_processed, !is.na(stress_event_type_overall)), 
                            aes(x = stress_event_intensity, y = "",
                            fill = "#ff3377", color = "#ff3377")) +
 ggridges::stat_binline(bins = 5, breaks = c(-0.05, 0.77, 1.59, 2.41, 3.23, 4.05), 
                        scale = 0.5, alpha = 0.5, lwd = 1, fatten = 1.5,
                         position = position_nudge(y = 0.18), draw_baseline = F, pad = F) +
  geom_boxplot(width = .15, alpha = .5, lwd = 1, fatten = 1.5, outlier.shape = NA,
                          size = 1.15, position = position_nudge(y = -0.25)) +
  geom_jitter(aes(color = "#ff3377"), alpha = 0.15, size = 0.8, height = 0.1) +
  coord_flip() +
  theme_cowplot() +
  scale_fill_manual(values = "#ff3377") +
  scale_color_manual(values = "#ff3377") +
    theme(
      legend.position = "none",
      axis.text.x = element_text(size = 16),
      axis.title.x = element_text(size = 18),
      axis.ticks.x = element_blank(),
      axis.text.y = element_text(size = 14),
      axis.title.y = element_text(size = 18)
    ) +
  labs(title = "", x = "Rating", y = "Stress Event Intensity") + 
  scale_x_continuous(breaks = c(0, 1, 2, 3, 4))
stress_level_plot
```

Now we can save them all together.

```{r}
# figure4 <- ggpubr::ggarrange(
#   event_freq_barplot, stress_level_plot, event_type_barplot,
#   ncol = 3,
#   nrow = 1,
#   widths = c(2, 2, 4),
#   labels = c("A", "B", "C"),
#   font.label = list(size = 20, face = "bold"), # Optional formatting
#   label.x = 0,
#   label.y = 1
# )
# figure4
# ggsave("figure4.jpg", figure4, width = 12, height = 6, dpi = 300)
```











## Figure 5: Raincloud Plots of Emotions

First we change the data into long format.

```{r}
emotion_items <- c("stress_state", "NA_state", "PA_state")
survey_long <- pivot_longer(survey_data_processed, cols = all_of(emotion_items),
                              names_to = "emotion", values_to = "rating")
survey_long <- survey_long %>%
  mutate(
    emotion = case_when(
      emotion == "stress_state" ~ "Stress",
      emotion == "NA_state" ~ "Negative Affect",
      emotion == "PA_state" ~ "Positive Affect"
    )
  )
```

Then we make our raincloud plot.

```{r}
colors <- c("#4575B4", "#1A9850", "#D73027")
emotion_raincloud_plot <- ggplot(survey_long, aes(x = rating, y = fct_relevel(emotion, "Stress",
                                        "Negative Affect", "Positive Affect"), fill = emotion, color = emotion)) +
  ggridges::stat_binline(bins = 5, scale = 0.3, alpha = 0.5, lwd = 1, fatten = 1.5,
                         position = position_nudge(y = 0.15), draw_baseline = F, pad = F) +
  geom_boxplot(width = .15, alpha = .5, lwd = 1, fatten = 1.5, outlier.shape = NA,
                          size = 1.15, position = position_nudge(y = -0.22)) +
  geom_jitter(aes(color = emotion), alpha = 0.15, size = 0.8, height = 0.05) +
  coord_flip() +
  theme_cowplot() +
  scale_fill_manual(values = colors) +
  scale_color_manual(values = colors) +
    theme(
      legend.position = "none",
      plot.title = element_text(size = 14.5, face = "bold", hjust = 0.5),
      axis.text.x = element_text(size = 18),
      axis.title.x = element_blank(),
      axis.text.y = element_text(size = 18),
      axis.title.y = element_text(size = 18)
    ) +
  labs(title = "", x = "Rating") +
  scale_x_continuous(breaks = 0:4)
emotion_raincloud_plot
```

```{r}
# ggsave("emotion_raincloud_plot.jpeg", emotion_raincloud_plot, device = "jpeg", width = 12, height = 10, dpi = 300)
```











## Figure 6: Raincloud plots for ddm variables, prop alc responses, and median rt

First we change the data into long format. These plots will have one value
for each subject session combination.

```{r}
k99_shared_data_3 <- k99_shared_data %>%
  group_by(subject, session) %>%
  mutate(
    prop_alc_responses = sum(response == "alc", na.rm = T) / 
      (sum(response == "alc", na.rm = T) + sum(response == "soft", na.rm = T)),
    median_rt = median(rt, na.rm = T)
  ) %>%
  slice(1)
```

```{r}
boundary_raincloud_plot <- plot_rc(k99_shared_data_3, k99_shared_data_3$B, 
                              "#907ad6", 1, .33, -.45, -0.17, 0.05, 0.75, 0.05)
boundary_raincloud_plot <- boundary_raincloud_plot + labs(title = "", x = "Decision Boundary", y = "") + 
  scale_x_continuous(breaks = seq(0, 4, by = 1)) + 
  xlim(0, 4)
boundary_raincloud_plot
```

```{r}
alcbias_raincloud_plot  <- plot_rc(k99_shared_data_3, k99_shared_data_3$alcbias, 
                                "#341671", 1, .33, -.45, -0.17, 0.05, .75, 0.05)
alcbias_raincloud_plot <- alcbias_raincloud_plot + labs(title = "", x = "Alcohol Bias", y = "") + 
  scale_x_continuous(breaks = seq(-5, 5, by = 1)) + xlim(-5, 5)
alcbias_raincloud_plot
```


```{r}
drift_raincloud_plot  <- plot_rc(k99_shared_data_3, k99_shared_data_3$drift, 
                                "#5a3f96", 1, .33, -.45, -0.17, 0.05, .75, 0.05)
drift_raincloud_plot <- drift_raincloud_plot + labs(title = "", x = "Drift Rate", y = "") + xlim(-1.5, 1.5)
drift_raincloud_plot
```

```{r}
nondec_raincloud_plot  <- plot_rc(k99_shared_data_3, k99_shared_data_3$nondectime, 
                                "#280659", 1, .33, -.45, -0.17, 0.05, 0.75, 0.05)
nondec_raincloud_plot <- nondec_raincloud_plot + labs(title = "", x = "Non-Decision Time", y = "") + 
  scale_x_continuous(breaks = seq(0, 1, by = .1)) + xlim(0, 1)
nondec_raincloud_plot
```

```{r}
rt_raincloud_plot <- plot_rc(k99_shared_data_3, k99_shared_data_3$median_rt, 
                                "#660f56", 1, .33, -.45, -0.17, 0.05, 0.75, 0.05)
rt_raincloud_plot <- rt_raincloud_plot + labs(title = "", x = "Median Response Time", y = "") +
                      xlim(0, 2)
rt_raincloud_plot
```


```{r}
response_raincloud_plot <- plot_rc(k99_shared_data_3, k99_shared_data_3$prop_alc_responses, 
                                "#ae2d68", 1, .33, -.45, -0.17, 0.05, 0.75, 0.05)
response_raincloud_plot <- response_raincloud_plot + labs(title = "", x = "Choices for Alcohol (%)", y = "") +
                          xlim(0, 1)
response_raincloud_plot
```


```{r}
figure6 <- ggpubr::ggarrange(
  response_raincloud_plot, rt_raincloud_plot, boundary_raincloud_plot,
  drift_raincloud_plot, alcbias_raincloud_plot, nondec_raincloud_plot,
  ncol = 2,
  nrow = 3,
  widths = c(2, 2),
  labels = c("E", "F", "G", "H", "I", "J"),
  font.label = list(size = 20, face = "bold"), # Optional formatting
  label.x = 0,
  label.y = 1
)
# figure6
# ggsave("figure6.jpg", figure6, width = 7.5, height = 12.5, dpi = 300)
```

## Combining Figures 4, 5, and 6

```{r}
figure10a <- ggpubr::ggarrange(
  figure4, emotion_raincloud_plot,
  ncol = 1,
  nrow = 2,
  labels = c("", "D"),
  font.label = list(size = 20, face = "bold"), # Optional formatting
  label.x = 0,
  label.y = 1
)

figure10 <- ggpubr::ggarrange(
  figure10a, figure6,
  ncol = 2,
  nrow = 1,
  widths = c(2.2, 1),
  font.label = list(size = 20, face = "bold"), # Optional formatting
  label.x = 0,
  label.y = 1
)
# ggsave("figure10.jpeg", figure10, device = "jpeg", width = 16, height = 10, dpi = 300)
```








## Figure 7: Distribution of prop alc responses and median rt by value function

We need to calculate the average response prop and average median rt
for each value in the value function.

```{r}
k99_shared_data_4 <- k99_shared_data %>%
  group_by(subject, session, value_function) %>%
  mutate(
    prop_alc_responses = sum(response == "alc", na.rm = T) / 
      (sum(response == "alc", na.rm = T) + sum(response == "soft", na.rm = T)),
    median_rt = median(rt, na.rm = T)
  ) %>% 
  slice(1)
k99_shared_data_4 <- k99_shared_data_4[c("subject", "session", "value_function",
                    "prop_alc_responses", "median_rt")]
```


```{r}
plot_value <- function(yvar, clr, clr2) {
  ggplot(k99_shared_data_4, aes(x = value_function, y = yvar, 
                                    fill = clr, color = clr, group = interaction(subject,session))) +
  geom_point(size = 2, alpha = 0.02) +
  geom_line(alpha = 0.02) +
  stat_summary(aes(group = 1), fun = mean, geom = "point", size = 5, color = clr2) +
  stat_summary(aes(group = 1), fun = mean, geom = "line", size = 2, color = clr2) + 
  theme_cowplot() +
  scale_fill_manual(values = clr) +
  scale_color_manual(values = clr) +
    theme(
      legend.position = "none",
      axis.text.x = element_text(size = 16),
      axis.title.x = element_text(size = 18),
      axis.ticks.x = element_blank(),
      axis.text.y = element_text(size = 14),
      axis.title.y = element_text(size = 18)
    ) +
  scale_x_continuous(breaks = seq(-3, 3, by = 1))
}
```


```{r}
response_value_plot <- plot_value(k99_shared_data_4$prop_alc_responses, "#ae2d68", "#7d274e")
response_value_plot <- response_value_plot + labs(title = "", x = "Value Function", y = "Choices for Alcohol (%)")
response_value_plot
```


```{r}
rt_value_plot <- plot_value(k99_shared_data_4$median_rt, "#660f56", "#421239")
rt_value_plot <- rt_value_plot + labs(title = "", x = "Value Function", y = "Median Response Time")
rt_value_plot
```

We see that people are less likely to choose alcohol when they indicated a lesser
baseline preference as expected. We also see they take a tiny bit longer (?) to
choose when they are more indifferent.

```{r}
figure7 <- ggpubr::ggarrange(
  response_value_plot, rt_value_plot,
  ncol = 1,
  nrow = 2,
  labels = c("A", "B"),
  font.label = list(size = 15, face = "bold"), # Optional formatting
  label.x = 0,
  label.y = 1
)
ggsave("figure7.jpg", figure7, width = 6, height = 8, dpi = 300)
```















##Figure 8: distribution of 6 vars by stress event


```{r}
k99_shared_data_5 <- k99_shared_data %>%
  group_by(subject, session, stress_event) %>%
  mutate(
    stress_prop_alc = sum(response == "alc", na.rm = T) / 
      (sum(response == "alc", na.rm = T) + sum(response == "soft", na.rm = T)),
    stress_median_rt = median(rt, na.rm = T),
    stress_boundary = mean(B),
    stress_bias = mean(alcbias),
    stress_drift = mean(drift),
    stress_nondec = mean(nondectime)
  ) %>% 
  slice(1)
k99_shared_data_5 <- k99_shared_data_5[c("subject", "stress_event", "stress_event_intensity",
                    "stress_prop_alc", "stress_median_rt",
                    "stress_boundary", "stress_bias",
                    "stress_drift", "stress_nondec")]
```

```{r}
plot_stress <- function(yvar, clr) {
  ggplot(k99_shared_data_5, aes(x = stress_event, y = yvar, 
                                    fill = clr, color = clr, group = subject)) +
  # geom_point(size = 2, alpha = 0.01) +
  geom_jitter(aes(color = clr), alpha = 0.03, size = 0.8, width = 0.15) +
  stat_summary(aes(group = 1), fun = mean, geom = "point", size = 5) +
  stat_summary(aes(group = 1), fun = mean, geom = "line", size = 1.25) + 
  theme_cowplot() +
  scale_fill_manual(values = clr) +
  scale_color_manual(values = clr) +
    theme(
      legend.position = "none",
      axis.text.x = element_text(size = 16),
      axis.title.x = element_text(size = 18),
      axis.ticks.x = element_blank(),
      axis.text.y = element_text(size = 14),
      axis.title.y = element_text(size = 18)
    ) +
  scale_x_discrete()
}
```


```{r}
rt_stress_plot <- plot_stress(k99_shared_data_5$stress_median_rt,"#660f56")
rt_stress_plot <- rt_stress_plot + ylim(0, 2) +
  labs(title = "", x = "Stress Event", y = "Median Response Time")
rt_stress_plot
```


```{r}
response_stress_plot <- plot_stress(k99_shared_data_5$stress_prop_alc,"#ae2d68")
response_stress_plot <- response_stress_plot + labs(title = "", x = "Stress Event", y = "Choices for Alcohol (%)")
response_stress_plot
```

We see that there is a difference in means.

```{r}
bias_stress_plot <- plot_stress(k99_shared_data_5$stress_bias,"#341671")
bias_stress_plot <- bias_stress_plot + ylim(-5, 5) +
  labs(title = "", x = "Stress Event", y = "Alcohol Bias")
bias_stress_plot
```


```{r}
boundary_stress_plot <- plot_stress(k99_shared_data_5$stress_boundary,"#907ad6")
boundary_stress_plot <- boundary_stress_plot + ylim(0, 4) +
  labs(title = "", x = "Stress Event", y = "Decision Boundary")
boundary_stress_plot
```

```{r}
drift_stress_plot <- plot_stress(k99_shared_data_5$stress_drift,"#5a3f96")
drift_stress_plot <- drift_stress_plot + ylim(-1.5, 1.5) +
  labs(title = "", x = "Stress Event", y = "Drift Rate")
drift_stress_plot
```


```{r}
nondec_stress_plot <- plot_stress(k99_shared_data_5$stress_nondec,"#280659")
nondec_stress_plot <- nondec_stress_plot + ylim(0, 1) + 
  labs(title = "", x = "Stress Event", y = "Non-Decision Time")
nondec_stress_plot
```

```{r}
# figure8 <- ggpubr::ggarrange(
#   response_stress_plot, rt_stress_plot, boundary_stress_plot, 
#   drift_stress_plot, bias_stress_plot, nondec_stress_plot,
#   ncol = 2, 
#   nrow = 3,
#   widths = c(2, 2),
#   labels = c("A", "B", "C", "D", "E", "F"),
#   font.label = list(size = 20, face = "bold"), # Optional formatting
#   label.x = 0,
#   label.y = 1 
# )
# ggsave("figure8.jpg", figure8, width = 7.5, height = 12.5, dpi = 300)
```













## Figure 9: Distribution of 6 vars by stress level

```{r}
k99_shared_data_6 <- k99_shared_data %>%
  group_by(subject, session, stress_state, na.rm = T) %>%
  mutate(
    stress_prop_alc = sum(response == "alc", na.rm = T) / 
      (sum(response == "alc", na.rm = T) + sum(response == "soft", na.rm = T)),
    stress_median_rt = median(rt, na.rm = T),
    stress_boundary = mean(B, na.rm = T),
    stress_bias = mean(alcbias, na.rm = T),
    stress_drift = mean(drift, na.rm = T),
    stress_nondec = mean(nondectime, na.rm = T)
  ) %>% 
  slice(1) 
k99_shared_data_6 <- k99_shared_data_6[c("subject", "session", "stress_state",
                    "stress_prop_alc", "stress_median_rt", "stress_boundary",
                    "stress_bias", "stress_drift", "stress_nondec")]

head(k99_shared_data_6)
```

```{r}
state_plot <- function(df, xvar, yvar, clr) { 
  ggplot(df, aes(x = xvar, y = yvar, fill = clr, color = clr)) +
  geom_jitter(aes(color = clr), alpha = 0.03, size = 0.8, width = 0.15) +
  geom_smooth(method = "lm") +
  theme_cowplot() +
  scale_fill_manual(values = clr) +
  scale_color_manual(values = clr) +
    theme(
      legend.position = "none",
      axis.text.x = element_text(size = 16),
      axis.title.x = element_text(size = 18),
      axis.ticks.x = element_blank(),
      axis.text.y = element_text(size = 14),
      axis.title.y = element_text(size = 18)
    ) +
  scale_x_continuous(breaks = seq(0, 4, by = 1))
}
```


```{r}
prop_stress_plot <- state_plot(k99_shared_data_6, k99_shared_data_6$stress_state, 
                k99_shared_data_6$stress_prop_alc,"#F7685C")
prop_stress_plot <- prop_stress_plot + ylim(0, 1) + 
  labs(title = "", x = "Stress State", y = "Choices for Alcohol (%)")
prop_stress_plot
```


```{r}
rt_stress_plot <- state_plot(k99_shared_data_6, k99_shared_data_6$stress_state, 
                k99_shared_data_6$stress_median_rt,"#E24942")
rt_stress_plot <- rt_stress_plot + ylim(0, 2) + 
  labs(title = "", x = "Stress State", y = "Median Response Time")
rt_stress_plot
```


```{r}
boundary_stress_plot <- state_plot(k99_shared_data_6, k99_shared_data_6$stress_state, 
                k99_shared_data_6$stress_boundary,"#D73027")
boundary_stress_plot <- boundary_stress_plot + ylim(0, 4) + 
  labs(title = "", x = "Stress State", y = "Decision Boundary")
boundary_stress_plot
```


```{r}
bias_stress_plot <- state_plot(k99_shared_data_6, k99_shared_data_6$stress_state, 
                k99_shared_data_6$stress_bias,"#a32d26")
bias_stress_plot <- bias_stress_plot + ylim(-5, 5) + 
  labs(title = "", x = "Stress State", y = "Alcohol Bias")
bias_stress_plot
```


```{r}
drift_stress_plot <- state_plot(k99_shared_data_6, k99_shared_data_6$stress_state, 
                k99_shared_data_6$stress_drift,"#b5332b")
drift_stress_plot <- drift_stress_plot + ylim(-1.5, 1.5) + 
  labs(title = "", x = "Stress State", y = "Drift Rate")
drift_stress_plot
```


```{r}
nondec_stress_plot <- state_plot(k99_shared_data_6, k99_shared_data_6$stress_state, 
                k99_shared_data_6$stress_nondec,"#7F1812")
nondec_stress_plot <- nondec_stress_plot + ylim(0, 1) + 
  labs(title = "", x = "Stress State", y = "Non-Decision Time")
nondec_stress_plot
```


```{r}
# figure9_stress <- ggpubr::ggarrange(
#   prop_stress_plot, rt_stress_plot, boundary_stress_plot, 
#   drift_stress_plot, bias_stress_plot, nondec_stress_plot,
#   ncol = 2, 
#   nrow = 3,
#   widths = c(2, 2),
#   labels = c("A", "B", "C", "D", "E", "F"),
#   font.label = list(size = 20, face = "bold"), # Optional formatting
#   label.x = 0,
#   label.y = 1 
# )
# ggsave("figure9_stress.jpg", figure9_stress, width = 8, height = 12, dpi = 300)
```



Now we repeat for NA.

```{r}
k99_shared_data_7 <- k99_shared_data %>%
  group_by(subject, session, NA_state, na.rm = T) %>%
  mutate(
    NA_prop_alc = sum(response == "alc", na.rm = T) / 
      (sum(response == "alc", na.rm = T) + sum(response == "soft", na.rm = T)),
    NA_median_rt = median(rt, na.rm = T),
    NA_boundary = mean(B, na.rm = T),
    NA_bias = mean(alcbias, na.rm = T),
    NA_drift = mean(drift, na.rm = T),
    NA_nondec = mean(nondectime, na.rm = T)
  ) %>% 
  slice(1)
k99_shared_data_7 <- k99_shared_data_7[c("subject", "session", "NA_state",
                    "NA_prop_alc", "NA_median_rt", "NA_boundary",
                    "NA_bias", "NA_drift", "NA_nondec")]
```


```{r}
prop_NA_plot <- state_plot(k99_shared_data_7, k99_shared_data_7$NA_state, 
                k99_shared_data_7$NA_prop_alc,"#91B7D9")
prop_NA_plot <- prop_NA_plot + ylim(0, 1) + 
  labs(title = "", x = "Negative Affect", y = "Choices for Alcohol (%)")
prop_NA_plot
```


```{r}
rt_NA_plot <- state_plot(k99_shared_data_7, k99_shared_data_7$NA_state, 
                k99_shared_data_7$NA_median_rt,"#6C99C9")
rt_NA_plot <- rt_NA_plot + ylim(0, 2) + 
  labs(title = "", x = "Negative Affect", y = "Median Response Time")
rt_NA_plot
```


```{r}
boundary_NA_plot <- state_plot(k99_shared_data_7, k99_shared_data_7$NA_state, 
                k99_shared_data_7$NA_boundary,"#4575B4")
boundary_NA_plot <- boundary_NA_plot + ylim(0, 4) + 
  labs(title = "", x = "Negative Affect", y = "Decision Boundary")
boundary_NA_plot
```


```{r}
bias_NA_plot <- state_plot(k99_shared_data_7, k99_shared_data_7$NA_state, 
                k99_shared_data_7$NA_bias,"#2C5D9C")
bias_NA_plot <- bias_NA_plot + ylim(-5, 5) + 
  labs(title = "", x = "Negative Affect", y = "Alcohol Bias")
bias_NA_plot
```


```{r}
drift_NA_plot <- state_plot(k99_shared_data_7, k99_shared_data_7$NA_state, 
                k99_shared_data_7$NA_drift,"#1B3E70")
drift_NA_plot <- drift_NA_plot + ylim(-1.5, 1.5) + 
  labs(title = "", x = "Negative Affect", y = "Drift Rate")
drift_NA_plot
```


```{r}
nondec_NA_plot <- state_plot(k99_shared_data_7, k99_shared_data_7$NA_state, 
                k99_shared_data_7$NA_nondec,"#0b2140")
nondec_NA_plot <- nondec_NA_plot + ylim(0, 1) + 
  labs(title = "", x = "Negative Affect", y = "Non-Decision Time")
nondec_NA_plot
```


```{r}
# figure9_NA <- ggpubr::ggarrange(
#   prop_NA_plot, rt_NA_plot, boundary_NA_plot, 
#   drift_NA_plot, bias_NA_plot, nondec_NA_plot,
#   ncol = 2, 
#   nrow = 3,
#   widths = c(2, 2),
#   labels = c("A", "B", "C", "D", "E", "F"),
#   font.label = list(size = 20, face = "bold"), # Optional formatting
#   label.x = 0,
#   label.y = 1 
# )
# ggsave("figure9_NA.jpg", figure9_NA, width = 8, height = 12, dpi = 300)
```



Now we repeat for PA.

```{r}
k99_shared_data_8 <- k99_shared_data %>%
  group_by(subject, session, PA_state, na.rm = T) %>%
  mutate(
    PA_prop_alc = sum(response == "alc", na.rm = T) / 
      (sum(response == "alc", na.rm = T) + sum(response == "soft", na.rm = T)),
    PA_median_rt = median(rt, na.rm = T),
    PA_boundary = mean(B, na.rm = T),
    PA_bias = mean(alcbias, na.rm = T),
    PA_drift = mean(drift, na.rm = T),
    PA_nondec = mean(nondectime, na.rm = T)
  ) %>% 
  slice(1)
k99_shared_data_8 <- k99_shared_data_8[c("subject", "session", "PA_state",
                    "PA_prop_alc", "PA_median_rt", "PA_boundary",
                    "PA_bias", "PA_drift", "PA_nondec")]
```


```{r}
prop_PA_plot <- state_plot(k99_shared_data_8, k99_shared_data_8$PA_state, 
                k99_shared_data_8$PA_prop_alc,"#7BC87C")
prop_PA_plot <- prop_PA_plot + ylim(0, 1) + 
  labs(title = "", x = "Positive Affect", y = "Choices for Alcohol (%)")
prop_PA_plot
```


```{r}
rt_PA_plot <- state_plot(k99_shared_data_8, k99_shared_data_8$PA_state, 
                k99_shared_data_8$PA_median_rt,"#4FBF64")
rt_PA_plot <- rt_PA_plot + ylim(0, 2) + 
  labs(title = "", x = "Positive Affect", y = "Median Response Time")
rt_PA_plot
```


```{r}
boundary_PA_plot <- state_plot(k99_shared_data_8, k99_shared_data_8$PA_state, 
                k99_shared_data_8$PA_boundary,"#1A9850")
boundary_PA_plot <- boundary_PA_plot + ylim(0, 4) + 
  labs(title = "", x = "Positive Affect", y = "Decision Boundary")
boundary_PA_plot
```


```{r}
bias_PA_plot <- state_plot(k99_shared_data_8, k99_shared_data_8$PA_state, 
                k99_shared_data_8$PA_bias,"#137F42")
bias_PA_plot <- bias_PA_plot + ylim(-5, 5) + 
  labs(title = "", x = "Positive Affect", y = "Alcohol Bias")
bias_PA_plot
```


```{r}
drift_PA_plot <- state_plot(k99_shared_data_8, k99_shared_data_8$PA_state, 
                k99_shared_data_8$PA_drift,"#0A5E2F")
drift_PA_plot <- drift_PA_plot + ylim(-1.5, 1.5) + 
  labs(title = "", x = "Positive Affect", y = "Drift Rate")
drift_PA_plot
```


```{r}
nondec_PA_plot <- state_plot(k99_shared_data_8, k99_shared_data_8$PA_state, 
                k99_shared_data_8$PA_nondec,"#054220")
nondec_PA_plot <- nondec_PA_plot + ylim(0, 1) + 
  labs(title = "", x = "Positive Affect", y = "Non-Decision Time")
nondec_PA_plot
```


```{r}
# figure9_PA <- ggpubr::ggarrange(
#   prop_PA_plot, rt_PA_plot, boundary_PA_plot, 
#   drift_PA_plot, bias_PA_plot, nondec_PA_plot,
#   ncol = 2, 
#   nrow = 3,
#   widths = c(2, 2),
#   labels = c("A", "B", "C", "D", "E", "F"),
#   font.label = list(size = 20, face = "bold"), # Optional formatting
#   label.x = 0,
#   label.y = 1 
# )
# ggsave("figure9_PA.jpg", figure9_PA, width = 8, height = 12, dpi = 300)
```


### Figure 10: Distribution of EMA Responses

We will plot the overall means/SE of the number of responses per day of EMA.
This is measured by the number of days after they completed the baseline.

We can calculate the day number using end_date_string (when they finished the
baseline survey) and the date variable for each survey.

*complete something after midnight?*

```{r}
# first we need to create a new df
ema_grid <- expand.grid(
  subject = 1:250,
  day_number = 1:14,
  daily_session = c("sess_1", "sess_2", "sess_3")
)
#add day num to merged with days since baseline
k99_shared_data_9 <- k99_shared_data %>%
  group_by(subject) %>%
  mutate(date = as.Date(date, format = "%Y-%m-%d"),
         baseline_date = as.Date(end_date_string, format = "%m/%d/%Y"),
         day_number = as.numeric(difftime(date, baseline_date, units = "days"))) %>%
  mutate(
    day_number = ifelse(day_number >= 1 & day_number <= 14, day_number, NA)
  ) %>% #there are 66000 NAs after this.
  group_by(subject, day_number) %>%
  mutate(num_completions = n_distinct(session),
         sess_1 = ifelse(num_completions >= 1, 1, 0),
         sess_2 = ifelse(num_completions >= 2, 1, 0),
         sess_3 = ifelse(num_completions >= 3, 1, 0)) %>%
  ungroup() %>%
  pivot_longer(cols = c("sess_1", "sess_2", "sess_3"),
               names_to = "daily_session",
               values_to = "session_complete")

k99_shared_data_9 <- k99_shared_data_9[c("subject", "day_number", "daily_session",
                                         "session_complete")]
k99_shared_data_9 <- unique(k99_shared_data_9)

ema_complete <- ema_grid %>%
  left_join(k99_shared_data_9, by = c("subject", "day_number", "daily_session"))

# there are some NAs because some did not have any sessions completed on a day
ema_complete[is.na(ema_complete)] <- 0
```


```{r}
ema_complete <- ema_complete %>%
  group_by(subject, day_number) %>%
  mutate(
    num_completions = sum(session_complete), .groups = "drop"
  ) %>%
  slice(1)
table(ema_complete$num_completions)
```

```{r}
clr = "#5c677d"
ema_dist_plot <- ggplot(ema_complete, aes(x = day_number, y = num_completions, 
                                    fill = clr, color = clr)) +
  geom_jitter(size = 2, alpha = 0.1, width = .35, height = .25) +
  stat_summary(aes(group = 1), fun = mean, geom = "point", size = 7, color = "black") +
  stat_summary(aes(group = 1), fun = mean, geom = "line", size = 3, color = "black") +
  theme_cowplot() +
  scale_fill_manual(values = clr) +
  scale_color_manual(values = clr) +
    theme(
      legend.position = "none",
      axis.text.x = element_text(size = 16),
      axis.title.x = element_text(size = 18),
      axis.ticks.x = element_blank(),
      axis.text.y = element_text(size = 14),
      axis.title.y = element_text(size = 18)
    ) +
  scale_x_continuous(breaks = seq(1, 14, by = 1)) +
  scale_y_continuous(breaks = seq(0, 3, by = .5)) +
  coord_cartesian(xlim = c(1, 14), ylim = c(-.25, 3.25)) +
  labs(title = "", x = "Day Number", y = "Number of EMA Assessments Completed")
ema_dist_plot
```


```{r}
# ggsave("ema_dist_plot.jpeg", ema_dist_plot, device = "jpeg", width = 9, 
#        height = 6, dpi = 300)
```















