---
title: "k99_data_exploration"
author: "Gavin Kelly"
date: "2025-07-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("C:/Users/gavin/OneDrive - andrew.cmu.edu/Documents/RADLab")
library(dplyr)
library(psych)
library(interactions)
library(ggplot2)
# k99_shared_data <- read.csv("k99_shared_data.csv")
```

```{r}
k99_shared_data_2 <- k99_shared_data %>%
  group_by(subject, session) %>%
  mutate(
    mean_prop_alc_responses = sum(response == "alc", na.rm = T) / 
      (sum(response == "alc", na.rm = T) + sum(response == "soft", na.rm = T)),
    mean_median_rt = median(rt, na.rm = T),
    alc_consumed = case_when(alc_today > 0 ~ 1,
                             TRUE ~ 0)
  ) %>%
    slice(1) %>%
  ungroup()
summary(lm(mean_prop_alc_responses ~ alc_consumed, data = k99_shared_data_2))
t.test(mean_prop_alc_responses ~ alc_consumed, data = k99_shared_data_2)
```


UPPS urgency - does it predict whether you drink, how much you drink, and prop alc?

```{r}
k99_shared_data_3 <- k99_shared_data_2 %>%
  group_by(subject) %>%
  mutate(prop_consumed = mean(alc_consumed, na.rm=T),
         average_consume = mean(alc_today, na.rm=T),
         average_prop_alc = mean(prop_alc_responses, na.rm = T)) %>%
  slice(1)
```


```{r}
#on the subject level, positive urgency seems to have no association with drinking
summary(lm(prop_consumed ~ upps_positive_urgency, data = k99_shared_data_3))
summary(lm(average_prop_alc ~ upps_negative_urgency, data = k99_shared_data_3))
```

```{r}
#negative urgency has no association with drinking or amount
summary(lm(prop_consumed ~ upps_negative_urgency, data = k99_shared_data_3))
summary(lm(average_consume ~ upps_negative_urgency, data = k99_shared_data_3))
```














How is NA state associated with drinking and prop responses?

Let's also create a time-lagged alc consumption variable to check this.

```{r}
# We see an association here with drinking and prop alc responses
# as NA state increases, drinking decreases
# however, the proportion of responses indicating preference to drink increases.
modTA <- lm(alc_today ~  NA_state, data = k99_dat_4)
summary(lm(alc_consumed ~ NA_state, data = k99_shared_data_2))
summary(lm(prop_alc_responses ~ NA_state, data = k99_shared_data_2))
summary(lm(alc_intend ~ NA_state, data = k99_shared_data_2))
```

```{r}
ggplot(k99_dat_4, aes(x = NA_state, y = alc_today)) + geom_jitter() +
  geom_smooth(method="lm")
```


```{r}
# PA is more important for high urgency people
modTPA <- lm(alc_today ~ PA_state * upps_positive_urgency, data = k99_dat_4)
probe_interaction(modTPA, pred = 'PA_state', modx = 'upps_positive_urgency')

# it seems people with high urgency are more effected by positive emotions.
# however, interestingly they have a bit lower likelihood to start drinking.
# It seems like people with high urgency need to be happy to drink, otherwise they wont.
# Further, they drink more than others when they are happy, and less than others when not.
modCPA <- lm(alc_consumed ~ upps_positive_urgency * PA_state, data = k99_shared_data_2)
probe_interaction(modCPA, pred = 'upps_positive_urgency', modx = 'PA_state')
# I think it's interesting that low urgency seems to have such an effect on the
# effect of PA on drinking, seems to show some good support for the theory.

# people low in urgency choose less alc when happy, but people high in urgency choose more
# i think its the same interaction but a different main effect
modPPA <- lm(prop_alc_responses ~ upps_positive_urgency * PA_state, data = k99_shared_data_2)
probe_interaction(modPPA, pred = 'upps_positive_urgency', modx = 'PA_state')
# It seems the (subconscious) perceived effect of positive emotion on alcohol use
# is more negative than the actual effect
```

```{r}
# let's see about only days when drinking occurs
k99_dat_4 <- k99_shared_data_2 %>% filter(alc_today >0)
modTPA <- lm(alc_today ~ upps_positive_urgency * PA_state, data = k99_dat_4)
probe_interaction(modTPA, pred = 'upps_positive_urgency', modx = 'PA_state')
# we see that people high in urgency drink a lot more
# their drinking also depends on their mood more.
# so there is main effect of urgency, as well as an interaction.
```



```{r}
modCNA <- lm(alc_consumed ~ upps_negative_urgency * stress_state, data = k99_shared_data_2)
probe_interaction(modCNA, pred = 'upps_negative_urgency', modx = 'stress_state')
summary(modCNA)
#it appears that when low in negative urgency, stress has a greater effect
# this is interestingly the opposite as we saw with positive urgency

#it seems stress impacts the likelihood to start drinking, while urgency impact amount
```
```{r}
modTNA <- lm(alc_today ~ stress_state * upps_negative_urgency, data = k99_dat_4)
probe_interaction(modTNA, pred = 'upps_negative_urgency', modx = 'stress_state')
summary(modTNA)
#stress increased drinking for people with low urgency, but decreases for people with high urgency
```

```{r}
modPNA <- lm(prop_alc_responses ~ upps_negative_urgency * stress_state, data = k99_shared_data_2)
probe_interaction(modPNA, pred = 'upps_negative_urgency', modx = 'stress_state')
# we just see a main effect of stress increasing drink choices
# while high urgency people still choose more, there is a reversed pattern.
# people experiencing NA want to drink more, but actually do it less.
# low NA may be seen as more neutral, or open to anything.
# they dont choose alcohol as much, but do end up drinking more.
# stress also seems to have a greater positive effect on people with low urgency
# on drinking days
# this may just show that people's perceptions of their behavior is very different from reality
```
























How do drinking motives predict momentary drinking and choices, and compare to baseline motives?

The only association between baseline motives and drinking behavior is coping increasing
average consumption. there is also coping and enhancement associated with alc choices.

It seems like there is not much association between drinking and motives.
However, there does seem to be a strong association with prop responses and momentary
enhancement and coping motives, both increasing choices.

The interaction between enhancement * PA_state and choices is also significant.

do baseline motives only matter based on a certain thing in the moment?

```{r}
summary(lm(average_prop_alc ~ dmq_social, data = k99_shared_data_3))
summary(lm(average_consume ~ dmq_enhancement, data = k99_shared_data_3))
```

# Coping motives associated with prop choices for alcohol, and drinks when you do drink
It is possible that this is a bias when people drink, they think now they have
higher coping motives. Maybe coping motives is somehow an outcome of drinking.
This may be supported by alc_intend being significant with coping motives.
There is only an interaction of prop choices for alcohol.

coping motives appear to be more associated with alc responses and intentions
than drinks already consumed. Could be worth doing a time lag to see motives from 
the day before, and how that predicts drinking behavior.

```{r}
summary(lm(alc_today ~  alc_mot_conform, data = k99_shared_data_2))
summary(lm(prop_alc_responses ~ alc_mot_coping * NA_state, data = k99_shared_data_2))
```

```{r}
#very small effects of enhancement
#it seems like baseline scores only matter when they are experiencing the given motive
#decent effects of social
#main effect of coping - increases drink amount
modTE <- lm(alc_today ~ alc_mot_coping * dmq_coping, data = k99_shared_data_2)
probe_interaction(modTE, pred = 'alc_mot_coping', modx = 'dmq_coping')
```

```{r}
#main effect coping
#main effect of enhancement decreasing likelihood of drinking - prob insignificant
#interaction of social increasing likelihood
modTE <- lm(alc_consumed ~ alc_mot_social * dmq_social, data = k99_shared_data_2)
probe_interaction(modTE, pred = 'alc_mot_social', modx = 'dmq_social')
```





Craving...

is positively associated with intentions to drink.

```{r}
cor.test(k99_shared_data_2$alc_craving, k99_shared_data_2$alc_intend)
```

These correlations show that the prop alc responses capture these variables pretty well.

```{r}
cor_df <- k99_shared_data_2[c("alc_craving", "prop_alc_responses", 
                               "alc_intend", "PA_change_alc",
                              "NA_change_alc", "stress_change_alc")]
cor_matrix2 <- cor_df %>%
  cor(use = "pairwise.complete.obs") %>% 
  round(., 2)
cor_matrix2
summary(lm(alc_craving ~ prop_alc_responses + alc_intend + PA_change_alc +
stress_change_alc + alc_exp_better_mood + alc_exp_relaxed, data = k99_shared_data_2))
```





