---
title: "k99_survey_data"
author: "Gavin Kelly"
date: "2025-06-04"
output: html_document
---

This is a data processing script for the k99 survey data.

I first rename all the variables. (lines 43-117)

I then combine the multiple response variables stress event type, motives, 
expectancies, and social context into one variable each. (lines 139-523)

I then mutate drink count, alc cue, and location variables. (lines 523-593)

I then do some sanity checks and save the csv. (lines 597-699)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("C:/Users/gavin/OneDrive - andrew.cmu.edu/Documents/RADLab")
```

## Load Packages

```{r}
library(dplyr)
library(lubridate)
library(ggplot2)
library(tidyr)
library(psych)
```

## Loading Data

```{r}
survey_data <- read.csv("survey_data.csv")
survey_data_og <- read.csv("survey_data.csv")
```

## View Variable Names

```{r}
# colnames(survey_data_og)
```

## Renaming Variables

```{r}
survey_data <- rename(survey_data, stress_event = q1StressfulEventResponse)

survey_data <- rename(survey_data, stress_event_type_argument = q2StressfulEventDescriptionoption1Response)
survey_data <- rename(survey_data, stress_event_type_social_dissapointment = q2StressfulEventDescriptionoption2Response)
survey_data <- rename(survey_data, stress_event_type_difficulty_work_school = q2StressfulEventDescriptionoption3Response)
survey_data <- rename(survey_data, stress_event_type_difficulty_home = q2StressfulEventDescriptionoption4Response)
survey_data <- rename(survey_data, stress_event_type_health_issue = q2StressfulEventDescriptionoption5Response)
survey_data <- rename(survey_data, stress_event_type_neg_event_to_others = q2StressfulEventDescriptionoption6Response)
survey_data <- rename(survey_data, stress_event_type_other = q2StressfulEventDescriptionoption7Response)

survey_data <- rename(survey_data, stress_event_intensity = q3StressfulEventRatingResponse)

survey_data <- rename(survey_data, stress_state = q4StressRatingResponse)
survey_data <- rename(survey_data, PA_state = q5PositivityRatingResponse)
survey_data <- rename(survey_data, NA_state = q6NegativityRatingResponse)

survey_data <- rename(survey_data, stress_change_alc = q7StressAfterAlcResponse)
survey_data <- rename(survey_data, stress_change_soft = q8StressAfterSoftResponse)

survey_data <- rename(survey_data, PA_change_alc = q9PositivityAfterAlcResponse)
survey_data <- rename(survey_data, PA_change_soft = q10PositivityAfterSoftResponse)
survey_data <- rename(survey_data, NA_change_alc = q11NegativityAfterAlcResponse)
survey_data <- rename(survey_data, NA_change_soft = q12NegativityAfterSoftResponse)

survey_data <- rename(survey_data, stress_state_change = q13StressChangeResponse)
survey_data <- rename(survey_data, PA_state_change = q14PositivityChangeResponse)
survey_data <- rename(survey_data, NA_state_change = q15NegativityChangeResponse)

survey_data <- rename(survey_data, alc_yday = q16AlcYesterdayResponse)
survey_data <- rename(survey_data, soft_yday = q17SoftYesterdayResponse)
survey_data <- rename(survey_data, alc_today = q18AlcTodayResponse)
survey_data <- rename(survey_data, soft_today = q19SoftTodayResponse)

survey_data <- rename(survey_data, alc_intend = q20AlcTodayRemainResponse)
survey_data <- rename(survey_data, soft_intend = q21SoftTodayRemainResponse)

survey_data <- rename(survey_data, thirst_state = q22ThirstyResponse)
survey_data <- rename(survey_data, hunger_state = q23HungryResponse)
survey_data <- rename(survey_data, tired_state = q24TiredResponse)
survey_data <- rename(survey_data, bored_state = q25BoredResponse)

survey_data <- rename(survey_data, alc_exp_relaxed = q26BehAfterAlcoption1Response)
survey_data <- rename(survey_data, alc_exp_sociable = q26BehAfterAlcoption2Response)
survey_data <- rename(survey_data, alc_exp_buzz = q26BehAfterAlcoption3Response)
survey_data <- rename(survey_data, alc_exp_better_mood = q26BehAfterAlcoption4Response)
survey_data <- rename(survey_data, alc_exp_energetic = q26BehAfterAlcoption5Response)
survey_data <- rename(survey_data, alc_exp_hangover = q26BehAfterAlcoption6Response)
survey_data <- rename(survey_data, alc_exp_embarrassed = q26BehAfterAlcoption7Response)
survey_data <- rename(survey_data, alc_exp_be_rude = q26BehAfterAlcoption8Response)
survey_data <- rename(survey_data, alc_exp_nauseous_vomit = q26BehAfterAlcoption9Response)
survey_data <- rename(survey_data, alc_exp_injury = q26BehAfterAlcoption10Response)
survey_data <- rename(survey_data, alc_exp_none = q26BehAfterAlcoption11Response)

survey_data <- rename(survey_data, alc_mot_coping = q27StatementsAfterAlcoption1Response)
survey_data <- rename(survey_data, alc_mot_social = q27StatementsAfterAlcoption2Response)
survey_data <- rename(survey_data, alc_mot_enhance = q27StatementsAfterAlcoption3Response)
survey_data <- rename(survey_data, alc_mot_none = q27StatementsAfterAlcoption4Response)

survey_data <- rename(survey_data, alc_craving = q28AlcCravingResponse)
survey_data <- rename(survey_data, soft_craving = q29SoftCravingResponse)

survey_data <- rename(survey_data, location = q30LocationResponse)

survey_data <- rename(survey_data, social_context_alone = q31Peopleoption1Response)
survey_data <- rename(survey_data, social_context_friend_roommate = q31Peopleoption2Response)
survey_data <- rename(survey_data, social_context_romantic_partner = q31Peopleoption3Response)
survey_data <- rename(survey_data, social_context_family = q31Peopleoption4Response)
survey_data <- rename(survey_data, social_context_coworker_classmate = q31Peopleoption5Response)
survey_data <- rename(survey_data, social_context_stranger = q31Peopleoption6Response)
survey_data <- rename(survey_data, social_context_other = q31Peopleoption7Response)

survey_data <- rename(survey_data, alc_cue = q32AlcNearByResponse)
survey_data <- rename(survey_data, responsibility = q33ResponsibilitiesResponse)
```

Now let's look at the data.

```{r}
# head(survey_data)
```

Looking at the data, we first need to mutate the variables so the response options
are Yes/No, and the names are more descriptive, for example:
stress_event_type_1 -> stress_event_type_argument.

We then need to combine the stress event types into one variable (stress_event_type_overall).
Same with alcohol expectancies, motives, and social context.

Then we can replace all empty strings with NA.

## Mutating Multiple Response Variables

First we need to combine the select multiple variables.

```{r}
survey_data$stress_event_type_overall <-   paste(survey_data$stress_event_type_argument, 
        survey_data$stress_event_type_social_dissapointment,
        survey_data$stress_event_type_difficulty_work_school, 
        survey_data$stress_event_type_difficulty_home,
        survey_data$stress_event_type_health_issue, 
        survey_data$stress_event_type_neg_event_to_others,
        survey_data$stress_event_type_other, sep = "")
```

```{r}
survey_data$alc_exp_overall <-   paste(survey_data$alc_exp_relaxed, 
        survey_data$alc_exp_sociable,
        survey_data$alc_exp_buzz, 
        survey_data$alc_exp_better_mood,
        survey_data$alc_exp_energetic, 
        survey_data$alc_exp_hangover,
        survey_data$alc_exp_embarrassed,
        survey_data$alc_exp_be_rude, 
        survey_data$alc_exp_nauseous_vomit,
        survey_data$alc_exp_injury, 
        survey_data$alc_exp_none, sep = "")
```

```{r}
survey_data$alc_mot_overall <- paste(survey_data$alc_mot_coping, 
        survey_data$alc_mot_social,
        survey_data$alc_mot_enhance, 
        survey_data$alc_mot_none, sep = "")
```

```{r}
survey_data$social_context_overall <-   paste(survey_data$social_context_alone, 
        survey_data$social_context_friend_roommate,
        survey_data$social_context_romantic_partner, 
        survey_data$social_context_family,
        survey_data$social_context_coworker_classmate, 
        survey_data$social_context_stranger,
        survey_data$social_context_other, sep = "")
```

Now, we can replace non-responses with NA.

```{r}
survey_data[survey_data == ""] <- NA
```

## Mutating Stress Event Type Variable

We can also make the overall stress event variable to be individual event/multiple.

```{r}
survey_data <- survey_data %>%
    mutate(
      stress_event_type_overall = case_when(
        (stress_event == "No" | is.na(stress_event)) ~ NA,
        stress_event_type_overall == "Argument, disagreement, or conflict" ~ "argument",
        stress_event_type_overall == "Social disappointment/let down" ~ "social_dissapointment",
        stress_event_type_overall == "Difficulties involving work or school" ~ "difficulty_work_school",
        stress_event_type_overall == "Difficulties at home" ~ "difficulty_home",
        stress_event_type_overall == "Health issue or accident" ~ "health_issue",
        stress_event_type_overall == "Negative event that happened to others" ~ "neg_event_to_others",
        stress_event_type_overall == "Other stressful event" ~ "other",
        is.na(stress_event_type_overall) ~ NA,
        TRUE ~ "multiple"
      )
    )
table(survey_data$stress_event_type_overall)
```

Now we can mutate the stress events to be only Yes or No responses.

```{r}
stopifnot((survey_data$stress_event_type_argument %in% c("Argument, disagreement, or conflict", NA)))
stopifnot((survey_data$stress_event_type_social_dissapointment %in% c("Social disappointment/let down", NA)))
stopifnot((survey_data$stress_event_type_difficulty_work_school %in% c("Difficulties involving work or school", NA)))
stopifnot((survey_data$stress_event_type_difficulty_home %in% c("Difficulties at home", NA)))
stopifnot((survey_data$stress_event_type_health_issue %in% c("Health issue or accident", NA)))
stopifnot((survey_data$stress_event_type_neg_event_to_others %in% c("Negative event that happened to others", NA)))
stopifnot((survey_data$stress_event_type_other %in% c("Other stressful event", NA)))

survey_data <- survey_data %>%
    mutate(
      stress_event_type_argument = case_when(
        (stress_event == "No" | is.na(stress_event)) ~ NA,
        stress_event_type_argument == "Argument, disagreement, or conflict" ~ "Yes",
        is.na(stress_event_type_overall) ~ NA,
        is.na(stress_event_type_argument) ~ "No"
      ),
      
      stress_event_type_social_dissapointment = case_when(
        (stress_event == "No" | is.na(stress_event)) ~ NA,
        stress_event_type_social_dissapointment == "Social disappointment/let down" ~ "Yes",
        is.na(stress_event_type_overall) ~ NA,
        is.na(stress_event_type_social_dissapointment) ~ "No"
      ),
      
      stress_event_type_difficulty_work_school = case_when(
        (stress_event == "No" | is.na(stress_event)) ~ NA,
        stress_event_type_difficulty_work_school == "Difficulties involving work or school" ~ "Yes",
        is.na(stress_event_type_overall) ~ NA,
        is.na(stress_event_type_difficulty_work_school) ~ "No"
      ),
      
      stress_event_type_difficulty_home = case_when(
        (stress_event == "No" | is.na(stress_event)) ~ NA,
        stress_event_type_difficulty_home == "Difficulties at home" ~ "Yes",
        is.na(stress_event_type_overall) ~ NA,
        is.na(stress_event_type_difficulty_home) ~ "No"
      ),
      
      stress_event_type_health_issue = case_when(
        (stress_event == "No" | is.na(stress_event)) ~ NA,
        stress_event_type_health_issue == "Health issue or accident" ~ "Yes",
        is.na(stress_event_type_overall) ~ NA,
        is.na(stress_event_type_health_issue) ~ "No"
      ),
      
      stress_event_type_neg_event_to_others = case_when(
        (stress_event == "No" | is.na(stress_event)) ~ NA,
        stress_event_type_neg_event_to_others == "Negative event that happened to others" ~ "Yes",
        is.na(stress_event_type_overall) ~ NA,
        is.na(stress_event_type_neg_event_to_others) ~ "No"
      ),
      
      stress_event_type_other = case_when(
        (stress_event == "No" | is.na(stress_event)) ~ NA,
        stress_event_type_other == "Other stressful event" ~ "Yes",
        is.na(stress_event_type_overall) ~ NA,
        is.na(stress_event_type_other) ~ "No"
      )
    )
```

Now the individual stress event responses are Yes/No.

## Mutating Alc Expectancy Variable

We can combine the expectancies into one variable.

```{r}
survey_data <- survey_data %>%
    mutate(
      alc_exp_overall = case_when(
        alc_exp_overall == "Feel more relaxed" ~ "relaxed",
        alc_exp_overall == "Be more sociable" ~ "sociable",
        alc_exp_overall == "Get a buzz" ~ "buzz",
        alc_exp_overall == "Be in a better mood" ~ "better_mood",
        alc_exp_overall == "Feel more energetic" ~ "energetic",
        alc_exp_overall == "Have a hangover" ~ "hangover",
        alc_exp_overall == "Do something that embarrasses you" ~ "embarrassed",
        alc_exp_overall == "Be rude or obnoxious" ~ "be_rude",
        alc_exp_overall == "Feel nauseous or vomit" ~ "nauseous_vomit",
        alc_exp_overall == "Hurt or injure yourself by accident" ~ "injury",
        alc_exp_overall == "None of these." ~ "none",
        is.na(alc_exp_overall) ~ NA,
        TRUE ~ "multiple"
      )
    )
table(survey_data$alc_exp_overall)
```

Now we can mutate the individual expectancies variables.

```{r}
stopifnot((survey_data$alc_exp_relaxed %in% c("Feel more relaxed", NA)))
stopifnot((survey_data$alc_exp_sociable %in% c("Be more sociable", NA)))
stopifnot((survey_data$alc_exp_buzz %in% c("Get a buzz", NA)))
stopifnot((survey_data$alc_exp_better_mood %in% c("Be in a better mood", NA)))
stopifnot((survey_data$alc_exp_energetic %in% c("Feel more energetic", NA)))
stopifnot((survey_data$alc_exp_hangover %in% c("Have a hangover", NA)))
stopifnot((survey_data$alc_exp_embarrassed %in% c("Do something that embarrasses you", NA)))
stopifnot((survey_data$alc_exp_be_rude %in% c("Be rude or obnoxious", NA)))
stopifnot((survey_data$alc_exp_nauseous_vomit %in% c("Feel nauseous or vomit", NA)))
stopifnot((survey_data$alc_exp_injury %in% c("Hurt or injure yourself by accident", NA)))
stopifnot((survey_data$alc_exp_none %in% c("None of these.", NA)))

survey_data <- survey_data %>%
    mutate(
      alc_exp_relaxed = case_when(
        alc_exp_relaxed == "Feel more relaxed" ~ "Yes",
        is.na(alc_exp_overall) ~ NA,
        is.na(alc_exp_relaxed) ~ "No"
      ),
      
      alc_exp_sociable = case_when(
        alc_exp_sociable == "Be more sociable" ~ "Yes",
        is.na(alc_exp_overall) ~ NA,
        is.na(alc_exp_sociable) ~ "No"
      ),
      
      alc_exp_buzz = case_when(
        alc_exp_buzz == "Get a buzz" ~ "Yes",
        is.na(alc_exp_overall) ~ NA,
        is.na(alc_exp_buzz) ~ "No"
      ),
      
      alc_exp_better_mood = case_when(
        alc_exp_better_mood == "Be in a better mood" ~ "Yes",
        is.na(alc_exp_overall) ~ NA,
        is.na(alc_exp_better_mood) ~ "No"
      ),
      
      alc_exp_energetic = case_when(
        alc_exp_energetic == "Feel more energetic" ~ "Yes",
        is.na(alc_exp_overall) ~ NA,
        is.na(alc_exp_energetic) ~ "No"
      ),
      
      alc_exp_hangover = case_when(
        alc_exp_hangover == "Have a hangover" ~ "Yes",
        is.na(alc_exp_overall) ~ NA,
        is.na(alc_exp_hangover) ~ "No"
      ),
      
      alc_exp_embarrassed = case_when(
        alc_exp_embarrassed == "Do something that embarrasses you" ~ "Yes",
        is.na(alc_exp_overall) ~ NA,
        is.na(alc_exp_embarrassed) ~ "No"
      ),
      
      alc_exp_be_rude = case_when(
        alc_exp_be_rude == "Be rude or obnoxious" ~ "Yes",
        is.na(alc_exp_overall) ~ NA,
        is.na(alc_exp_be_rude) ~ "No"
      ),
      
      alc_exp_nauseous_vomit = case_when(
        alc_exp_nauseous_vomit == "Feel nauseous or vomit" ~ "Yes",
        is.na(alc_exp_overall) ~ NA,
        is.na(alc_exp_nauseous_vomit) ~ "No"
      ),
      
      alc_exp_injury = case_when(
        alc_exp_injury == "Hurt or injure yourself by accident" ~ "Yes",
        is.na(alc_exp_overall) ~ NA,
        is.na(alc_exp_injury) ~ "No"
      ),
      
      alc_exp_none = case_when(
        alc_exp_none == "None of these." ~ "Yes",
        is.na(alc_exp_overall) ~ NA,
        is.na(alc_exp_none) ~ "No"
      )
    )
```

## Mutating Drinking Motives Variable

We can combine motives into one variable.

```{r}
survey_data <- survey_data %>%
    mutate(
      alc_mot_overall = case_when(
        alc_mot_overall == "You would drink to forget your worries or problems." ~ "coping",
        alc_mot_overall == "You would drink to celebrate a special occasion with friends." ~ "social",
        alc_mot_overall == "You would drink because you like the feeling." ~ "enhance",
        alc_mot_overall == "None of these." ~ "none",
        is.na(alc_mot_overall) ~ NA,
        TRUE ~ "multiple"
      )
    )
table(survey_data$alc_mot_overall)
```

Now we can mutate the individual motives variables.

```{r}
stopifnot((survey_data$alc_mot_coping %in% c("You would drink to forget your worries or problems.", NA)))
stopifnot((survey_data$alc_mot_social %in% c("You would drink to celebrate a special occasion with friends.", NA)))
stopifnot((survey_data$alc_mot_enhance %in% c("You would drink because you like the feeling.", NA)))
stopifnot((survey_data$alc_mot_none %in% c("None of these.", NA)))

survey_data <- survey_data %>%
    mutate(
      alc_mot_coping = case_when(
        alc_mot_coping == "You would drink to forget your worries or problems." ~ "Yes",
        is.na(alc_mot_overall) ~ NA,
        is.na(alc_mot_coping) ~ "No"
      ),
      
      alc_mot_social = case_when(
        alc_mot_social == "You would drink to celebrate a special occasion with friends." ~ "Yes",
        is.na(alc_mot_overall) ~ NA,
        is.na(alc_mot_social) ~ "No"
      ),
      
      alc_mot_enhance = case_when(
        alc_mot_enhance == "You would drink because you like the feeling." ~ "Yes",
        is.na(alc_mot_overall) ~ NA,
        is.na(alc_mot_enhance) ~ "No"
      ),
      
      alc_mot_none = case_when(
        alc_mot_none == "None of these." ~ "Yes",
        is.na(alc_mot_overall) ~ NA,
        is.na(alc_mot_none) ~ "No"
      )
    )
```

## Mutating Social Company Variable

We can combine social company into one variable.

```{r}
survey_data <- survey_data %>%
    mutate(
      social_context_overall = case_when(
        social_context_overall == "No one (I am alone)" ~ "alone",
        social_context_overall == "Friend(s)/Roommate(s)" ~ "friend_roommate",
        social_context_overall == "Romantic partner(s)" ~ "romantic_partner",
        social_context_overall == "Family member(s)" ~ "family",
        social_context_overall == "Coworker(s)/Classmate(s)" ~ "coworker_classmate",
        social_context_overall == "Stranger(s)" ~ "stranger",
        social_context_overall == "Other" ~ "other",
        is.na(social_context_overall) ~ NA,
        TRUE ~ "multiple"
      )
    )
table(survey_data$social_context_overall)
```

Now we can mutate the individual variables.

```{r}
stopifnot((survey_data$social_context_alone %in% c("No one (I am alone)", NA)))
stopifnot((survey_data$social_context_friend_roommate %in% c("Friend(s)/Roommate(s)", NA)))
stopifnot((survey_data$social_context_romantic_partner %in% c("Romantic partner(s)", NA)))
stopifnot((survey_data$social_context_family %in% c("Family member(s)", NA)))
stopifnot((survey_data$social_context_coworker_classmate %in% c("Coworker(s)/Classmate(s)", NA)))
stopifnot((survey_data$social_context_stranger %in% c("Stranger(s)", NA)))
stopifnot((survey_data$social_context_other %in% c("Other", NA)))


survey_data <- survey_data %>%
    mutate(
      social_context_alone = case_when(
        social_context_alone == "No one (I am alone)" ~ "Yes",
        is.na(social_context_overall) ~ NA,
        is.na(social_context_alone) ~ "No"
      ),
      
      social_context_friend_roommate = case_when(
        social_context_friend_roommate == "Friend(s)/Roommate(s)" ~ "Yes",
        is.na(social_context_overall) ~ NA,
        is.na(social_context_friend_roommate) ~ "No"
      ),
      
      social_context_romantic_partner = case_when(
        social_context_romantic_partner == "Romantic partner(s)" ~ "Yes",
        is.na(social_context_overall) ~ NA,
        is.na(social_context_romantic_partner) ~ "No"
      ),
      
      social_context_family = case_when(
        social_context_family == "Family member(s)" ~ "Yes",
        is.na(social_context_overall) ~ NA,
        is.na(social_context_family) ~ "No"
      ),
      
      social_context_coworker_classmate = case_when(
        social_context_coworker_classmate == "Coworker(s)/Classmate(s)" ~ "Yes",
        is.na(social_context_overall) ~ NA,
        is.na(social_context_coworker_classmate) ~ "No"
      ),
      
      social_context_stranger = case_when(
        social_context_stranger == "Stranger(s)" ~ "Yes",
        is.na(social_context_overall) ~ NA,
        is.na(social_context_stranger) ~ "No"
      ),
      
      social_context_other = case_when(
        social_context_other == "Other" ~ "Yes",
        is.na(social_context_overall) ~ NA,
        is.na(social_context_other) ~ "No"
      )
    )
```

## Mutating Number of Drink Variables

The number of drinks should be from 0-10. I checked and only alc_yday and soft_yday 
have 10+ recorded, so I will fix those.

```{r}
survey_data <- survey_data %>%
  mutate(
    alc_yday = case_when(
      alc_yday == "10+" ~ "10",
      TRUE ~ alc_yday
    ),
    
    soft_yday = case_when(
      soft_yday == "10+" ~ "10",
      TRUE ~ soft_yday
    ),
    
    alc_yday = as.integer(alc_yday),
    soft_yday = as.integer(soft_yday),
    alc_today = as.integer(alc_today),
    soft_today = as.integer(soft_today),
    alc_intend = as.integer(alc_intend),
    soft_intend = as.integer(soft_intend)
  )
```

## Mutating Alc Cue Variable

```{r}
survey_data <- survey_data %>%
  mutate(
    alc_cue = case_when(
      alc_cue == "Alcohol is visible directly (bottle, glass, etc.)" ~ "directly_visible",
      alc_cue == "Alcohol is visible indirectly (TV, magazine, etc.)" ~ "indirectly_visible",
      alc_cue == "No alcohol is visible" ~ "none"
    )
  )
stopifnot(survey_data$alc_cue %in% c(
  "directly_visible",
  "indirectly_visible",
  "none",
  NA
))
```


## Mutating location variable

```{r}
survey_data <- survey_data %>%
  mutate(
    location = case_when(
      location == "School/work" ~ "school_work",
      location == "Home" ~ "home",
      location == "Someone else’s home" ~ "someone_elses_home",
      location == "Restaurant/café" ~ "restaurant_cafe",
      location == "Outdoors" ~ "outdoors",
      location == "Other location" ~ "other",
      location == "Bar/club" ~ "bar_club",
      NA ~ NA
    )
  )
stopifnot(survey_data$location %in% c("school_work", "home", "someone_elses_home",
                              "outdoors", "other", "bar_club", "restaurant_cafe", NA))
head(survey_data)
```

## Sanity Checks for Categorical Variables

There are 0 NA responses for stress_event. There are the same # of Nos for this
variable as NAs for all the stress event specific variables. 

I checked the values of each variable as well, and they all look good. 
As the values for session increase, they are decreasing in frequency.

## Sanity Checks for Numeric Variables

We need to check these numeric variables: subject, session, stress_event_intensity,
stress_state, PA_state, NA_state, stress_change_alc, stress_change_soft, PA_change_alc,
PA_change_soft, NA_change_alc, NA_change_soft, stress_change, PA_change, NA_change,
alc_yday, soft_yday, alc_today, soft_today, alc_intend, soft_intend, thirst_state,
hunger_state, tired_state, bored_state, alc_craving, soft_craving.

```{r}
### subject and session

stopifnot(survey_data$subject %in% c(1:250))
stopifnot(survey_data$session %in% c(1:45))

### state ratings

stopifnot(survey_data$stress_event_intensity %in% c(0:4) | 
            is.na(survey_data$stress_event_intensity))
stopifnot(survey_data$stress_state %in% c(0:4) | 
            is.na(survey_data$stress_state))
stopifnot(survey_data$PA_state %in% c(0:4) | 
            is.na(survey_data$PA_state))
stopifnot(survey_data$NA_state %in% c(0:4) | 
            is.na(survey_data$NA_state))

### stress change after drink

stopifnot(survey_data$stress_change_alc %in% c(-2:2) | 
            is.na(survey_data$stress_change_alc))
stopifnot(survey_data$stress_change_soft %in% c(-2:2) | 
            is.na(survey_data$stress_change_soft))

### PA change after drink

stopifnot(survey_data$PA_change_alc %in% c(-2:2) | 
            is.na(survey_data$PA_change_alc))
stopifnot(survey_data$PA_change_soft %in% c(-2:2) | 
            is.na(survey_data$PA_change_soft))

### NA change after drink

stopifnot(survey_data$NA_change_alc %in% c(-2:2) | 
            is.na(survey_data$NA_change_alc))
stopifnot(survey_data$NA_change_soft %in% c(-2:2) | 
            is.na(survey_data$NA_change_soft))

### general emotion changes

stopifnot(survey_data$stress_state_change %in% c(-2:2) | 
            is.na(survey_data$stress_state_change))
stopifnot(survey_data$PA_state_change %in% c(-2:2) | 
            is.na(survey_data$PA_state_change))
stopifnot(survey_data$NA_state_change %in% c(-2:2) | 
            is.na(survey_data$NA_state_change))

### drink amounts

stopifnot(survey_data$alc_yday %in% c(0:10) | 
            is.na(survey_data$alc_yday))
stopifnot(survey_data$soft_yday %in% c(0:10) | 
            is.na(survey_data$soft_yday))
stopifnot(survey_data$alc_today %in% c(0:10) | 
            is.na(survey_data$alc_today))
stopifnot(survey_data$soft_today %in% c(0:10) | 
            is.na(survey_data$soft_today))
stopifnot(survey_data$alc_intend %in% c(0:10) | 
            is.na(survey_data$alc_intend))
stopifnot(survey_data$soft_intend %in% c(0:10) | 
            is.na(survey_data$soft_intend))

### physical states

stopifnot(survey_data$thirst_state %in% c(0:4) | 
            is.na(survey_data$thirst_state))
stopifnot(survey_data$hunger_state %in% c(0:4) | 
            is.na(survey_data$hunger_state))
stopifnot(survey_data$tired_state %in% c(0:4) | 
            is.na(survey_data$tired_state))
stopifnot(survey_data$bored_state %in% c(0:4) | 
            is.na(survey_data$bored_state))

### craving 

stopifnot(survey_data$alc_craving %in% c(0:4) | 
            is.na(survey_data$alc_craving))
stopifnot(survey_data$soft_craving %in% c(0:4) | 
            is.na(survey_data$soft_craving))
```


Now we can save the survey data as a csv.

```{r}
write.csv(survey_data, "survey_data_processed.csv", row.names = F)
```











