---
title: "k99_choicetask_data"
author: "Gavin Kelly"
date: "2025-06-03"
output: html_document
---

This is the data processing script for the k99 choicetask data.

I first rename the variables. (lines 39-49)
I then add rt and day of week variables, and change alc position to a chr. (lines 53-101)
I then review the sanity checks and final df, and save it to files (commented out). (lines 104-118)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("C:/Users/gavin/OneDrive - andrew.cmu.edu/Documents/RADLab")
```

## Load Packages

```{r}
library(dplyr)
library(lubridate)
library(ggplot2)
library(tidyr)
library(psych)
```

## Loading Data

```{r}
choicetask_data <- read.csv("choicetask_data.csv")
baseline_data <- read.csv("baseline_data_processed.csv")
```

## View Variable Names

```{r}
# colnames(choicetask_data)
```

First we can rename the variables.

```{r}
choicetask_data <- rename(choicetask_data, computer_platform = computer.platform)
choicetask_data <- rename(choicetask_data, trial = trialnum)
choicetask_data <- rename(choicetask_data, alc_position = alcPosition)
choicetask_data <- rename(choicetask_data, alc_image = alcImage)
choicetask_data <- rename(choicetask_data, rating_alc = ratingAlc)
choicetask_data <- rename(choicetask_data, soft_image = softImage)
choicetask_data <- rename(choicetask_data, rating_soft = ratingSoft)
```


Initially looking at the data, we need to change position to a left/right chr,
we need to change the latency to seconds rather than milliseconds,
and we could calculate a rating difference between the two options.

```{r}
choicetask_data$rt <- choicetask_data$latency / 1000
choicetask_data$latency <- NULL

choicetask_data$alc_position <- as.character(choicetask_data$alc_position)
choicetask_data <- choicetask_data %>%
  mutate(
    alc_position = case_when(
      alc_position == "1" ~ "left",
      TRUE ~ "right"
    )
  )

choicetask_data$value_function <- choicetask_data$rating_alc - choicetask_data$rating_soft
```

If the response time is greater than 4 seconds, we will set the RT and response to NA.

```{r}
choicetask_data <- choicetask_data %>%
  mutate(
    response = case_when(
      rt > 4 ~ NA,
      response == "0" ~ NA,
      TRUE ~ response
    )
  )

choicetask_data <- choicetask_data %>%
  mutate(
    rt = case_when(
      rt > 4 ~ NA,
      TRUE ~ rt
    )
  )

# It appears there are 4307 responses that exceeded 4 seconds.
# This means there are 966741 valid responses (sum(!is.na(choicetask_data$response)))
```

We can also calculate day of week using the lubridate package and the date variable.

```{r}
choicetask_data$day_of_week <- wday(choicetask_data$date, label = T)
```

Add vars for prop alc responses and median rt.

```{r}
choicetask_data <- choicetask_data %>%
  group_by(subject, session) %>%
  mutate(
    prop_alc_responses = sum(response == "alc", na.rm = T) / 
      (sum(response == "alc", na.rm = T) + sum(response == "soft", na.rm = T)),
    median_rt = median(rt, na.rm = T)
  )
```

We will add variable counting the prop rt <300ms for each session

```{r}
choicetask_data <- choicetask_data %>%
  group_by(subject) %>%
  mutate(
    rt_fast_prop = sum(rt < .3, na.rm = T) / sum(!is.na(response), na.rm = T)
  )
```

Add afternoon/evening variable

```{r}
choicetask_data <- choicetask_data %>%
  mutate(
    hour = hour(hms(time)),
    time_of_day = case_when(
      hour >= 0 & hour < 8 ~ "evening",
      hour >= 8 & hour < 18 ~ "afternoon",
      hour >= 18 & hour < 24 ~ "evening",
      TRUE ~ "other"
    )
  )
choicetask_data$hour <- NULL
```


```{r}
# head(choicetask_data)
```

I also double checked that computer_platform, date, time rating_alc, rating_soft, subject,
session, trial, alc_position, alc_image, and soft_image all contained only the 
expected data. Meaning that it was in the expected range, only expected values, with no NA values.

There are 800 NA responses in the rt variable, and 5104 in the response variable.

Now we can save the choicetask data as a csv.

```{r}
# write.csv(choicetask_data, "choicetask_data_processed.csv", row.names = F)
```










