---
title: "k99_analysis_data"
author: "Gavin Kelly"
date: "2025-06-19"
output: html_document
---

This script is used to prepare the shared k99.2 data for analysis.

## First we will explain the variables in the shared data set.

Column 1: Variable to identify participants 1-250.

Columns 2-62: EMA Assessment Variables.

  stress_event: did a stressful event occur in the last 30 minutes? yes/no
  
  stress_event_type_: specific types of stressful events (yes/no) as well as
  an overall variable with each type of stressful event included.
  
  *The next three variables also exist for PA and NA*
  
  stress_state: variable for stress level at time of assessment completion.
  
  stress_change_(alc or soft): if you were to consume (alc or soft) later today,
  how would your stress change?
  
  stress_state_change: How has your stress changed since the last
  assessment you completed?
  
  *the next three variables also exist for soft drinks. We capped responses at 10*
  
  alc_yday: Number of alcoholic drinks consumed yesterday.
  
  alc_today: Number of alcoholic drinks consumed today.
  
  alc_intend: Number of alcoholic drinks you intend to drink the rest of the day.
  
  thirst, hunger, tired, bored state: ratings of physiological states.
  
  alc_exp_: specific types of alcohol expectancies (yes/no) as well as
  an overall variable with each type of alcohol expectancy included.
  
  alc_mot_: specific types of drinking motives (yes/no) as well as
  an overall variable with each type of drinking motive included.
  
  alc_craving and soft_craving: Craving ratings for types of beverages.
  
  location: where participants were at time of assessment.
  
  social_context_: specific types of social contexts (yes/no) as well as
  an overall variable with each possible social context included.
  
  alc_cue: whether alcohol is directly (e.g. bottle) or indirectly (e.g. TV ad) visible.
  
  responsibility: whether participants had any responsibilities right now, later
  today, or tomorrow morning.

Columns 63-79: Choice Task Variables (choice task completed once per assessment).

  date and time: when the choice task was begun (and EMA assessment completed).
  
  trial: maximum of 160 trials (choices made) possibly completed after each EMA assessment.
  
  alc_position: which side of the screen the alcoholic beverage was on, with the soft
  drink on the other side.
  
  alc_image and soft_image: which drinks were presented for each choice/trial.
  
  rating_alc and rating_soft: the baseline ratings of the drinks presented.
  
  response: whether the participant chose the alcoholic or non-alcoholic beverage for each trial.
  
  rt: how fast a choice was made in seconds.
  
  value_function: the difference in ratings between the alcoholic and 
  non-alcoholic beverage (alc - soft).
  
  prop_alc_responses: the proportion of choices the participant made for alcohol
  in a given assessment, aka one time completing the choice task.
  
  median_rt: the median response time in seconds for a given assessment.
  
  rt_fast_prop: the proportion of response times < 300ms for a subject across the whole study.
  
  time_of_day: whether the assessment was completed in the afternoon (8:00-18:00)
  or the evening (18:00-8:00)

Columns 80-83: DDM Parameters.
  
  drift: the drift rate parameter.
  
  alcbias: the alcohol bias parameter.
  
  B: the decision boundary parameter.
  
  nondectime: the non-decision time parameter.

Columns 84-270: Baseline Variables.

  progress: % of baseline completed.
  
  duration_minutes: how long the baseline took each participant to complete.
  
  finished: whether the participant fully completed the baseline.
  
  sex: Participants' sex assigned at birth.
  
  student: Whether the participant is a student.
  
  education: Education level of participants.
  
  employment: Employment classification of participants.
  
  audit_1, audit_2...: Scores for individual items of AUDIT survey.
  
  dmq_1, dmq_2...: Scores for individual items of DMQ survey.
  
  upps_1, upps_2...: Scores for individual items of UPPS survey.
  
  cerq_1, cerq_2...: Scores for individual items of CERQ survey.
  
  ers_1, ers_2...: Scores for individual items of ERS survey.
  
  alc01, alc02...: Ratings of each alcoholic drink.
  
  soft01, soft02...: Ratings of each non-alcoholic drink.
  
  end_date_string: The date when the baseline was completed.
  
  age: The age of each participant.
  
  audit_score: Sum score of individual audit items.
  
  audit_risk_class: low (0-3), risky (4-9), harmful (10-13), severe (14+)
  
  dmq_social, etc.: average scores for each DMQ subscale.
  
  upps_negative_urgency, upps_positive urgency: average scores for UPPS subscales.
  
  cerq_self_blame, etc.: average scores for each CERQ subscale.
  
  ers_persistence, etc.: average scores for each ERS subscale.
  
  race: variable with individual races, and multiple if more than one selected.
  
  gender: variable with multiple gender options, and multiple if more than one selected.
  
  sexuality: variable with multiple sexuality options, and multiple if more than one selected.

The script is organized by sections, with one section for each model.

## We will give an overview of each section of the script.

First we filter the data, retaining only what we need for analysis. (lines 176-216)

Then we prepare the data for the 4 primary models, stress event, stress state,
NA state, PA state. (lines 217-243)

We then prepare the data for the models 5-13 for anticipated change in emotion and
perceived change in emotion. (lines 243-299)

Finally, we prepare the data for the model that uses baseline predictors. (lines 300-341)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("C:/Users/gavin/OneDrive - andrew.cmu.edu/Documents/RADLab")
library(dplyr)
```

```{r}
#load the publicly available data
# k99_shared_data <- read.csv("k99_shared_data.csv")
```

### Filter responses and overwrite Prop Alc Responses and Median rt Variables

```{r}
k99_shared_data <- k99_shared_data %>%
  mutate(response = case_when(
    rt < 0.3 ~ NA,
    TRUE ~ response
  ))
k99_shared_data <- k99_shared_data %>%
  group_by(subject, session) %>%
  mutate(
    prop_alc_responses = sum(response == "alc", na.rm = T) / 
      (sum(response == "alc", na.rm = T) + sum(response == "soft", na.rm = T)),
    median_rt = median(rt, na.rm = T)
  )
```

```{r}
k99_shared_data <- k99_shared_data %>%
  group_by(subject, session) %>%
  slice(1)
```

Option: exclude people with prop fast rt (<300ms) > 10%. This removes 25 people.
Just replace k99_shared_data with k99_slow_data in the next code chunk to use this.

```{r}
# k99_slow_data <- k99_shared_data %>%
#   filter(rt_fast_prop < 0.1)
```

### Filter Data

We will keep variables that are relevant for analysis. We will include rt_fast_prop,
but will remove it for primary analyses, and may use it to filter later on (see line ).

```{r}
k99_filtered_data <- k99_shared_data[,names(k99_shared_data) %in% c("subject", "stress_event", "stress_event_type_argument", "stress_event_type_social_dissapointment", "stress_event_type_difficulty_work_school", "stress_event_type_difficulty_home", "stress_event_type_health_issue", "stress_event_type_neg_event_to_others", "stress_event_type_other", "stress_event_intensity", "stress_state", "PA_state", "NA_state", "stress_change_alc", "stress_change_soft", "PA_change_alc", "PA_change_soft", "NA_change_alc", "NA_change_soft", "stress_state_change", "PA_state_change", "NA_state_change", "alc_yday", "soft_yday", "alc_today", "soft_today", "alc_intend", "soft_intend", "thirst_state", "hunger_state", "tired_state", "bored_state", "alc_exp_relaxed", "alc_exp_sociable", "alc_exp_buzz", "alc_exp_better_mood", "alc_exp_energetic", "alc_exp_hangover", "alc_exp_embarrassed", "alc_exp_be_rude", "alc_exp_nauseous_vomit", "alc_exp_injury", "alc_mot_coping", "alc_mot_social", "alc_mot_enhance", "alc_craving", "soft_craving", "location", "social_context_alone", "social_context_friend_roommate", "social_context_romantic_partner", "social_context_family", "social_context_coworker_classmate", "social_context_stranger", "social_context_other", "alc_cue", "responsibility", "stress_event_type_overall", "alc_exp_overall", "alc_mot_overall", "social_context_overall", "day_of_week", 'time_of_day', "median_rt", "prop_alc_responses", "rt_fast_prop", "B", "drift", "alcbias", "nondectime")]
```

Get data on the session level.

## Stress binary event model

```{r}
k99_stress_binary_data <- k99_filtered_data[,!names(k99_filtered_data) %in% c("stress_state", "PA_state", "NA_state", "stress_change_alc", "stress_change_soft", "PA_change_alc", "PA_change_soft", "NA_change_alc", "NA_change_soft", "stress_state_change", "PA_state_change", "NA_state_change",
"stress_event_type_argument", "stress_event_type_social_dissapointment", "stress_event_type_difficulty_work_school", "stress_event_type_difficulty_home", "stress_event_type_health_issue", "stress_event_type_neg_event_to_others", "stress_event_type_other", "stress_event_intensity", "stress_event_type_overall", "alc_exp_overall", "alc_mot_overall", "social_context_overall", "rt_fast_prop", "nondectime")]
```

## Stress State model

```{r}
k99_stress_state_data <- k99_filtered_data[,!names(k99_filtered_data) %in% c("stress_event", "PA_state", "NA_state", "stress_change_alc", "stress_change_soft", "PA_change_alc", "PA_change_soft", "NA_change_alc", "NA_change_soft", "stress_state_change", "PA_state_change", "NA_state_change", "stress_event_type_argument", "stress_event_type_social_dissapointment", "stress_event_type_difficulty_work_school", "stress_event_type_difficulty_home", "stress_event_type_health_issue", "stress_event_type_neg_event_to_others", "stress_event_type_other", "stress_event_intensity", "stress_event_type_overall", "alc_exp_overall", "alc_mot_overall", "social_context_overall", "rt_fast_prop", "nondectime")]
```

## NA State model

```{r}
k99_na_state_data <- k99_filtered_data[,!names(k99_filtered_data) %in% c("stress_event", "stress_state", "PA_state", "stress_change_alc", "stress_change_soft", "PA_change_alc", "PA_change_soft", "NA_change_alc", "NA_change_soft", "stress_state_change", "PA_state_change", "NA_state_change", "stress_event_type_argument", "stress_event_type_social_dissapointment", "stress_event_type_difficulty_work_school", "stress_event_type_difficulty_home", "stress_event_type_health_issue", "stress_event_type_neg_event_to_others", "stress_event_type_other", "stress_event_intensity", "stress_event_type_overall", "alc_exp_overall", "alc_mot_overall", "social_context_overall", "rt_fast_prop", "nondectime")]
```

## PA State model

```{r}
k99_pa_state_data <- k99_filtered_data[,!names(k99_filtered_data) %in% c("stress_event", "stress_state", "NA_state", "stress_change_alc", "stress_change_soft", "PA_change_alc", "PA_change_soft", "NA_change_alc", "NA_change_soft", "stress_state_change", "PA_state_change", "NA_state_change", "stress_event_type_argument", "stress_event_type_social_dissapointment", "stress_event_type_difficulty_work_school", "stress_event_type_difficulty_home", "stress_event_type_health_issue", "stress_event_type_neg_event_to_others", "stress_event_type_other", "stress_event_intensity", "stress_event_type_overall", "alc_exp_overall", "alc_mot_overall", "social_context_overall", "rt_fast_prop", "nondectime")]
```

## Prospective Change Models

# Stress Change Alc

```{r}
k99_stress_change_alc <- k99_filtered_data[,!names(k99_filtered_data) %in% c("stress_event", "stress_state", "NA_state", "PA_state", "stress_change_soft", "PA_change_alc", "PA_change_soft", "NA_change_alc", "NA_change_soft", "stress_state_change", "PA_state_change", "NA_state_change", "stress_event_type_argument", "stress_event_type_social_dissapointment", "stress_event_type_difficulty_work_school", "stress_event_type_difficulty_home", "stress_event_type_health_issue", "stress_event_type_neg_event_to_others", "stress_event_type_other", "stress_event_intensity", "stress_event_type_overall", "alc_exp_overall", "alc_mot_overall", "social_context_overall", "rt_fast_prop", "nondectime")]
```

# Stress Change Soft

```{r}
k99_stress_change_soft <- k99_filtered_data[,!names(k99_filtered_data) %in% c("stress_event", "stress_state", "NA_state", "PA_state", "stress_change_alc", "PA_change_alc", "PA_change_soft", "NA_change_alc", "NA_change_soft", "stress_state_change", "PA_state_change", "NA_state_change", "stress_event_type_argument", "stress_event_type_social_dissapointment", "stress_event_type_difficulty_work_school", "stress_event_type_difficulty_home", "stress_event_type_health_issue", "stress_event_type_neg_event_to_others", "stress_event_type_other", "stress_event_intensity", "stress_event_type_overall", "alc_exp_overall", "alc_mot_overall", "social_context_overall", "rt_fast_prop", "nondectime")]
```

# PA Change Alc

```{r}
k99_pa_change_alc <- k99_filtered_data[,!names(k99_filtered_data) %in% c("stress_event", "stress_state", "NA_state", "PA_state", "stress_change_soft", "stress_change_alc", "PA_change_soft", "NA_change_alc", "NA_change_soft", "stress_state_change", "PA_state_change", "NA_state_change", "stress_event_type_argument", "stress_event_type_social_dissapointment", "stress_event_type_difficulty_work_school", "stress_event_type_difficulty_home", "stress_event_type_health_issue", "stress_event_type_neg_event_to_others", "stress_event_type_other", "stress_event_intensity", "stress_event_type_overall", "alc_exp_overall", "alc_mot_overall", "social_context_overall", "rt_fast_prop", "nondectime")]
```

# PA Change soft

```{r}
k99_pa_change_soft <- k99_filtered_data[,!names(k99_filtered_data) %in% c("stress_event", "stress_state", "NA_state", "PA_state", "stress_change_alc", "stress_change_soft", "PA_change_alc", "NA_change_alc", "NA_change_soft", "stress_state_change", "PA_state_change", "NA_state_change", "stress_event_type_argument", "stress_event_type_social_dissapointment", "stress_event_type_difficulty_work_school", "stress_event_type_difficulty_home", "stress_event_type_health_issue", "stress_event_type_neg_event_to_others", "stress_event_type_other", "stress_event_intensity", "stress_event_type_overall", "alc_exp_overall", "alc_mot_overall", "social_context_overall", "rt_fast_prop", "nondectime")]
```

# NA Change alc

```{r}
k99_na_change_alc <- k99_filtered_data[,!names(k99_filtered_data) %in% c("stress_event", "stress_state", "NA_state", "PA_state", "stress_change_alc", "stress_change_soft", "PA_change_alc", "PA_change_soft", "NA_change_soft", "stress_state_change", "PA_state_change", "NA_state_change", "stress_event_type_argument", "stress_event_type_social_dissapointment", "stress_event_type_difficulty_work_school", "stress_event_type_difficulty_home", "stress_event_type_health_issue", "stress_event_type_neg_event_to_others", "stress_event_type_other", "stress_event_intensity", "stress_event_type_overall", "alc_exp_overall", "alc_mot_overall", "social_context_overall", "rt_fast_prop", "nondectime")]
```

# NA Change soft

```{r}
k99_na_change_soft <- k99_filtered_data[,!names(k99_filtered_data) %in% c("stress_event", "stress_state", "NA_state", "PA_state", "stress_change_alc", "stress_change_soft", "PA_change_alc", "PA_change_soft", "NA_change_alc", "stress_state_change", "PA_state_change", "NA_state_change", "stress_event_type_argument", "stress_event_type_social_dissapointment", "stress_event_type_difficulty_work_school", "stress_event_type_difficulty_home", "stress_event_type_health_issue", "stress_event_type_neg_event_to_others", "stress_event_type_other", "stress_event_intensity", "stress_event_type_overall", "alc_exp_overall", "alc_mot_overall", "social_context_overall", "rt_fast_prop", "nondectime")]
```

## Perceived Change Models

# Perceived Stress Change

```{r}
k99_perceived_stress_change <- k99_filtered_data[,!names(k99_filtered_data) %in% c("stress_event", "stress_state", "NA_state", "PA_state", "stress_change_alc", "stress_change_soft", "PA_change_alc", "PA_change_soft", "NA_change_alc", "NA_change_soft", "PA_state_change", "NA_state_change", "stress_event_type_argument", "stress_event_type_social_dissapointment", "stress_event_type_difficulty_work_school", "stress_event_type_difficulty_home", "stress_event_type_health_issue", "stress_event_type_neg_event_to_others", "stress_event_type_other", "stress_event_intensity", "stress_event_type_overall", "alc_exp_overall", "alc_mot_overall", "social_context_overall", "rt_fast_prop", "nondectime")]
```

# Perceived PA Change

```{r}
k99_perceived_pa_change <- k99_filtered_data[,!names(k99_filtered_data) %in% c("stress_event", "stress_state", "NA_state", "PA_state", "stress_change_alc", "stress_change_soft", "PA_change_alc", "PA_change_soft", "NA_change_alc", "NA_change_soft", "stress_state_change", "NA_state_change", "stress_event_type_argument", "stress_event_type_social_dissapointment", "stress_event_type_difficulty_work_school", "stress_event_type_difficulty_home", "stress_event_type_health_issue", "stress_event_type_neg_event_to_others", "stress_event_type_other", "stress_event_intensity", "stress_event_type_overall", "alc_exp_overall", "alc_mot_overall", "social_context_overall", "rt_fast_prop", "nondectime")]
```

# Perceived NA Change

```{r}
k99_perceived_na_change <- k99_filtered_data[,!names(k99_filtered_data) %in% c("stress_event", "stress_state", "NA_state", "PA_state", "stress_change_alc", "stress_change_soft", "PA_change_alc", "PA_change_soft", "NA_change_alc", "NA_change_soft", "PA_state_change", "stress_state_change", "stress_event_type_argument", "stress_event_type_social_dissapointment", "stress_event_type_difficulty_work_school", "stress_event_type_difficulty_home", "stress_event_type_health_issue", "stress_event_type_neg_event_to_others", "stress_event_type_other", "stress_event_intensity", "stress_event_type_overall", "alc_exp_overall", "alc_mot_overall", "social_context_overall", "rt_fast_prop", "nondectime")]
```

## Baseline Characteristics Model

We will not include audit risk class.

```{r}
#keep variables that are relevant for analysis
k99_baseline_predictors <- k99_shared_data[,names(k99_shared_data) %in% c("subject", "median_rt",  "prop_alc_responses", "B", "drift", "alcbias",
"age", "student", "audit_score", "dmq_social", "dmq_coping", "dmq_enhancement", "dmq_conformity", "upps_negative_urgency", "upps_positive_urgency", "cerq_self_blame", "cerq_acceptance", "cerq_rumination", "cerq_positive_refocusing", "cerq_planning_refocusing", "cerq_reappraisal", "cerq_perspective", "cerq_catastrophizing", "cerq_blaming_others", "ers_persistence", "ers_sensitivity", "ers_intensity", "race", "gender", "sexuality", "sex", "education", "employment")]
```

## Saving all 14 Data Frames as .csv files for input to the models

```{r}
# write.csv(k99_stress_binary_data, "k99_stress_binary_data.csv", row.names = F)
# 
# write.csv(k99_stress_state_data, "k99_stress_state_data.csv", row.names = F)
# 
# write.csv(k99_na_state_data, "k99_na_state_data.csv", row.names = F)
# 
# write.csv(k99_pa_state_data, "k99_pa_state_data.csv", row.names = F)
# 
# write.csv(k99_stress_change_alc, "k99_stress_change_alc.csv", row.names = F)
# 
# write.csv(k99_stress_change_soft, "k99_stress_change_soft.csv", row.names = F)
# 
# write.csv(k99_na_change_alc, "k99_na_change_alc.csv", row.names = F)
# 
# write.csv(k99_na_change_soft, "k99_na_change_soft.csv", row.names = F)
# 
# write.csv(k99_pa_change_alc, "k99_pa_change_alc.csv", row.names = F)
# 
# write.csv(k99_pa_change_soft, "k99_pa_change_soft.csv", row.names = F)
# 
# write.csv(k99_perceived_stress_change, "k99_perceived_stress_change.csv", row.names = F)
# 
# write.csv(k99_perceived_na_change, "k99_perceived_na_change.csv", row.names = F)
# 
# write.csv(k99_perceived_pa_change, "k99_perceived_pa_change.csv", row.names = F)
# 
# write.csv(k99_baseline_predictors, "k99_baseline_predictors.csv", row.names = F)
```


















